---
title: "KPI Forecasts 2019"
output: html_notebook
---

### Reportbacks
#### Summary
```{r warning=FALSE, echo=FALSE, message=FALSE, fig.width=11, fig.height=6}
library(knitr)
library(kableExtra)
options(knitr.kable.NA = '')
```

* 2018 had signficantly more reportbacks than our historical trend. Hence the model predicts mean reversion to historical growth rates, leading to a forecast that is not significantly higher than this year's total
```{r warning=FALSE, echo=FALSE, message=FALSE}
kable_styling(kable(forecastRB, digits=3))
```

#### Visual
* X axis shows the progression of the year, by day, Y axis shows the cumulative sum of reportbacks
* Solid lines are actual cumulative sums of reportbacks over time, dotted lines are the trend lines
```{r warning=FALSE, echo=FALSE, message=FALSE, fig.width=13, fig.height=7}
pRBForecast
```

### MAMs
####Summary
* For MAMs, we show 4 forecasts
    * With or without bertly previews
    * The type of forecast, one shows the simple trend forecast, the other assumes 2% month over month growth
    * For all 4, we show the average actual MAMs across 2018 and the forecast average in 2019
* We see that the trend line over time is essentially flat
```{r warning=FALSE, echo=FALSE, message=FALSE}
kable_styling(kable(forecastsMAM, digits=3))
```

#### Visual
* X axis shows the month and year, Y axis shows MAMs for the month
* Dashed lines are trend lines over time
* Blue dashed line is the 2% month over month growth model
* Dotted line simply shows the expected MAMs in December 2019
```{r warning=FALSE, echo=FALSE, message=FALSE, fig.width=18, fig.height=8}
grid.arrange(pnew, pold, ncol=2, top=textGrob('MAMs Over Time',gp=gpar(fontsize=15)))
```

