---
output: html_notebook
---

#### MAM Investigation

* Summary
	* Overall seasonal pattern appears to be holding, with activity increasing from Feb to March
	* However, this March left us with fewer MAM than last year
	* The reduction in MAM is primarily in non-niche members as niche has similar number of active members
	* Total number of actions taken by all members is actually *higher* this March than last
	* This pattern holds for niche and non-niche, though fewer niche account creations were compensated for by more repeat niche engagement
	* Action composition shows more activity over web and fewer accounts created

```{r warning=FALSE, echo=FALSE, message=FALSE}
library(scales)

mm <- 
  read_csv('../Data/MAM_breakdown.csv') %>% 
  setNames(c('month','return_user','niche','count')) %>% 
  filter(month != '2017-04') %>% 
  mutate(
    niche = ifelse(niche=='Yes', 'Niche', 'Non-Niche')
    ) 
act <- 
  read_csv('../Data/action_breakdown.csv') %>% 
  setNames(c('month', 'action_type', 'niche', 'count')) %>% 
  mutate(
    niche = ifelse(niche=='Yes', 'Niche', 'Non-Niche')
    ) %>% 
  filter(month != '2017-04') %>% 
  group_by(month, niche) %>% 
  mutate(
    prop = count/sum(count),
    Text = percent(prop), 
    position = 1-cumsum(prop) + (.5*prop)
    )
act.N <- 
  read_csv('../Data/action_breakdown.csv') %>% 
  setNames(c('month', 'action_type', 'niche', 'count')) %>% 
  mutate(niche = ifelse(niche=='Yes', 'Niche', 'Non-Niche')) %>% 
  filter(month != '2017-04') %>% 
  group_by(month, action_type) %>% 
  summarise(
    count = sum(count)
  ) %>% 
  mutate(
    prop = count/sum(count),
    Text = percent(prop), 
    position = 1-cumsum(prop) + (.5*prop)
  )
```

#### Deeper Dive

* We see an increase from Feb but not as much as last year
```{r warning=FALSE, echo=FALSE, fig.width=11, fig.height=6.5}
labs <- mm %>% group_by(month) %>% summarise(count=sum(count))
ggplot(mm, aes(x=month, y=count)) + 
  geom_bar(stat='identity') + 
  ggtitle('Overall Trend') + 
  geom_text(data = labs, aes(x=month, label=count, y=count), vjust=-1, size=2.5) + 
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  theme(plot.title=element_text(hjust=.5)) 
```
* Pivoting by Niche and New/Returning
	* Niche overall active looks comparable to last year
	  * A 3:1 new:repeat ratio in niche has given way to roughly 45:55 ratio
	* Most of the decline appears to be among non-niche, occuring in both new and repeat
	  * Ratio of new:repeat is not very different
```{r warning=FALSE, echo=FALSE, fig.width=18, fig.height=6.5}
ggplot(mm, aes(x=month, y=count, fill=return_user)) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust = 0.5), aes(label=count), size=2.5) +
  stat_summary(fun.y = sumIf, aes(label = ..y.., group = month), geom = "text", vjust=-.2) +
  facet_wrap(~niche) + 
  scale_y_continuous(breaks=pretty_breaks(16)) +
  scale_fill_brewer(palette="Set2")
```
* Pivoting by Action Types
	* Very interesting that the total number of actions taken is actually a bit higher than last year
	* This suggests we have fewer people taking more actions
	* Account creations are down but website utilization is up
```{r warning=FALSE, echo=FALSE, fig.width=16, fig.height=6.5}
act.agg <- act %>% group_by(month, action_type) %>% summarise(count = sum(count))
ggplot(act.agg, aes(x=month, y=count, fill=reorder(action_type, count))) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust=.5), aes(label=count), vjust=0, size=2.5) +
  stat_summary(fun.y = sumIf, aes(label = ..y.., group = month), geom = "text", vjust=-.2) +
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  ggtitle('Action Counts') + 
  theme(plot.title=element_text(hjust=.5)) + 
  guides(fill=guide_legend(title="Action Type")) +
  scale_fill_brewer(palette="Set2")
```
* Splitting by Niche
  * Both niche and non-niche show the same pattern of slightly more activity this March
  * Similar action type breakdowns as overall with fewer new accounts, but more site activity
```{r warning=FALSE, echo=FALSE, fig.width=18, fig.height=6.5}
ggplot(act, aes(x=month, y=count, fill=reorder(action_type, count))) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust = 0.5), aes(label=count), vjust=0, size=2.5) +
  stat_summary(fun.y = sumIf, aes(label = ..y.., group = month), geom = "text", vjust=-.3) +
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  ggtitle('Action Counts') + facet_wrap(~niche) + 
  theme(plot.title=element_text(hjust=.5)) + 
  guides(fill=guide_legend(title="Action Type")) +
  scale_fill_brewer(palette="Set2")
```
* Activity composition 
  * Activity breakdown delta shows up even more clearly here; lots more website activity
```{r warning=FALSE, echo=FALSE, fig.width=16, fig.height=6.5}
ggplot(act.N, aes(x=month, y=prop, fill=reorder(action_type, prop))) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust=.5), aes(label=Text), size=2.5) +
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  theme(plot.title=element_text(hjust=.5)) + 
  labs(y='Proportion', title='Action Composition') +
  guides(fill=guide_legend(title="Action Type")) +
  scale_fill_brewer(palette="Set2")
```
* Splitting by Niche
  * Same story holds when breaking out niche and non-niche
```{r warning=FALSE, echo=FALSE, fig.width=18, fig.height=6.5}
ggplot(act, aes(x=month, y=prop, fill=reorder(action_type, prop))) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust=.5), aes(label=Text), size=3) +
  facet_wrap(~niche) + 
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  labs(title='Action Composition', y='Proportion') + 
  theme(plot.title=element_text(hjust=.5)) +
  guides(fill=guide_legend(title="Action Type")) +
  scale_fill_brewer(palette="Set2")
```

```{r echo=FALSE, warning=FALSE, message=FALSE,fig.width=16, fig.height=6.5}
# 
# melMon <- 
#   read_csv('../Data/MAM_Forecast_Breakdown_03022018.csv') %>% 
#   setNames(c('yearMonth','return_user','distinctNS')) %>% 
#   filter(!yearMonth %in% c('2015-12','2017-04') & !grepl('2018', yearMonth)) %>% 
#   mutate(
#     new_user = ifelse(return_user=='Yes', 0, 1),
#     date = as.Date(paste0(yearMonth, '-01'), format='%Y-%m-%d'),
#     year = year(date),
#     month = month(date)
#   ) %>% 
#   group_by(year, month) %>% 
#   summarise(
#     t = sum(distinctNS)
#   ) %>% 
#   mutate(p=t/sum(t)) %>% 
#   group_by(month) %>%
#   mutate(
#     monthMean = mean(p)
#   ) %>% ungroup() %>% 
#   mutate(
#     quarter = 
#       case_when(month %in% 1:3 ~ 1,
#                 month %in% 4:6 ~ 2, 
#                 month %in% 7:9 ~ 3, 
#                 TRUE ~ 4)
#   ) %>% 
#   group_by(quarter) %>% 
#   mutate(
#     quarterMean = mean(p)
#   )
# 
# ggplot(melMon, aes(x=as.factor(month), y=p, fill=as.factor(year))) +
#   geom_bar(stat='identity', position='dodge') +
#   geom_line(aes(y=monthMean, group=year), linetype='dotted', size=.3) +
#   geom_point(aes(y=monthMean, group=year)) +
#   # geom_point(aes(y=quarterMean, group=year), shape=3) + 
#   geom_hline(yintercept = 1/12) + 
#   annotate("text", x=1/12, y=1/12, vjust = -1, hjust=-.1, size=2.2, 
#            label = "Even Distribution Mark") +
#   scale_fill_brewer(palette='Set2') + 
#   scale_y_continuous(breaks=pretty_breaks(10)) + 
#   guides(fill=guide_legend(title="Year")) +
#   labs(title='Active Member Distribution Within Year', x='Month', y='Proportion') +
#   theme(plot.title=element_text(hjust=.5))

```


```{r warning=FALSE, echo=FALSE, message=FALSE, fig.width=12, fig.height=6.5}
# da <-
#   read_csv('../Data/daily_active_members.csv') %>%
#   setNames(c('date','users')) %>%
#   filter(!is.na(users) & date != '2017-04-06') %>% 
#   mutate(
#     DayOfWeek = factor(weekdays(date),
#                        levels=c('Monday','Tuesday','Wednesday','Thursday',
#                                 'Friday','Saturday','Sunday'))
#   )
# 
# ggplot(da, aes(x=date, y=users, colour=DayOfWeek)) + 
#   geom_point() + 
#   scale_x_date(breaks=pretty_breaks(16)) +
#   theme(plot.title=element_text(hjust=.5)) + 
#   scale_colour_brewer(palette='YlGnBu') +
#   ggtitle('Users Per Day Over Time')
```

