---
title: "Crash Text Dummy Analysis"
output: html_notebook
---

###Summary
#####Key Takeaways:
1. There is clear evidence of the effectiveness of the campaign in reducing the frequency of texting and driving
2. The effectiveness dampens over time, but does persist even on a 4-8 week horizon
    a) We see this by constructing a difference in difference table where we see the change in likelihood to text and drive before and after the campaign for folks who were surveyed 72 hours and 4-8 weeks after the campaign. This is compared to the change in the control group to calculate the change for participants and removing exogenous drift in likelihood
    b) We see that the effect of the campaign in the first 72 hours is an 11.5% reduction in texting and driving
    c) We also see that the effect of the campaign in the 4-8 week period after falls to a reduction of about 1.6%
```{r message=FALSE, warning=FALSE, echo=FALSE}
#Load required packages and custom functions
library(rpart)
library(rpart.plot)
library(caret)
library(ROCR)
library(scales)
library(knitr)
source('~/Data/AdHoc/Scripts/init.R')
source('~/Data/AdHoc/Scripts/DSUtils.R')
options(knitr.kable.NA = '')

#Write and execute functions to prepare individual files
prepControl <- function(path) {
  ctdControl <- 
    read_csv(path) %>%
    tbl_dt() %>%
    setNames(
      c('timestamp','gender','geography','licenseType','driveFrequency','intervenedFriend',
        'intervenedFamily','textDriveFreq','textDriveDanger','email')
    ) %>%
    mutate(
      group = 'Control'
    )
  return(ctdControl)
}

prep4_8 <- function(path) {
  ctd4_8 <- 
    read_csv(path) %>%
    tbl_dt() %>%
    setNames(
      c('timestamp','gender','geography','licenseType','driveFrequency','intervenedFriend',
        'intervenedFamily','textDriveFreq','textDriveDanger','takeAction')
    ) %>%
    mutate(
      group = '4-8 Weeks'
    )
  return(ctd4_8)
}

prep72 <- function(path) {
  
  ctd72 <- 
    read_csv(path) %>%
    tbl_dt() %>% 
    setNames(
      c('timestamp','gender','geography','licenseType','driveFrequency','intervenedFriend',
        'intervenedFamily','textDriveFreq','textDriveDanger','ctdStrategies','ctd.willInterveneFriend',
        'ctd.willInterveneFamily','takeAction')
    ) %>%
    mutate(
      group = '72 Hours'
    )
  
  return(ctd72)
}

#Combine Files into one file with flags
prepData <- function(pathControl, pathExp1, pathExp2) {
  control <- prepControl(pathControl)
  ctd4_8 <- prep4_8(pathExp1)
  ctd72 <- prep72(pathExp2)
  
  ctd <- 
    rbind(control, ctd4_8, ctd72, fill=T) %>%
    mutate(
      date = as.Date(substr(timestamp, 1,10), format='%Y/%m/%d')
    ) %>%
    tbl_dt()
  
  return(ctd)
  
}

ctd <- 
  prepData(
    '~/Data/AdHoc/Data/Crash Text Dummy - Control.csv', 
    '~/Data/AdHoc/Data/Crash Text Dummy - 4-8 Weeks.csv', 
    '~/Data/AdHoc/Data/Crash Text Dummy - 72 Hours.csv'
    )

ages <- read_csv('~/Data/AdHoc/Data/email_age_ctd.csv')

#Re-label variables for ease of use and removing rare levels
#Create Additional useful fields
textDriveTable<- ctd[,.N,by=textDriveFreq]
genderTable <- ctd[,.N,by=gender]

ctd %<>%
  mutate(
    textDrive.yn = ifelse(textDriveFreq=="I don't drive", NA, 
                                  ifelse(textDriveFreq=='Never', 0, 1)),
    textDrive = factor(ifelse(grepl('Only', textDriveFreq), 'Sometimes', textDriveFreq), levels=c('Often','Sometimes','Never')),
    licenseType = ifelse(licenseType=="Driver's license", 'License', 
                         ifelse(licenseType=="Driver's permit", 'Permit', 'Neither')),
    gender = ifelse(gender=='Man', 'Male', 
                    ifelse(gender=='Woman', 'Female', 'Other/DNR')),
    intervenedFriend = ifelse(!(intervenedFriend %in% c('No','Yes')), 'NotApplicable', intervenedFriend),
    intervenedFamily = ifelse(!(intervenedFriend %in% c('No','Yes')), 'NotApplicable', intervenedFamily),
    #Factors in R are numbers with labels. We can use this to display characters variables in the order we want. 
    #Below, I turn "group" into a factor so it always displays in the order specified
    group = factor(group, levels=c('Control','72 Hours','4-8 Weeks')),
    timePeriod = ifelse(date < '2017-03-21', 'Before', 'After')
  ) %>%
  left_join(ages, copy=T)

surveyDist <- 
  ggplot(ctd, aes(x=group,y=date)) + 
  geom_violin(position='dodge',aes(fill=group)) + 
  coord_flip() + theme(legend.position="none") + 
  ggtitle('Survey Date by Group') + 
  theme(plot.title = element_text(hjust = 0.5))
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
DnD <- function(data, pivot) {
  
  DnD <-
    data %>%
    filter(!is.na(get(pivot))) %>%
    group_by(group, timePeriod) %>%
    summarise(
      Frequency = mean(get(pivot))
    ) %>%
    spread(timePeriod, Frequency, fill=ctd[group=='Control' & timePeriod=='Before',mean(get(pivot), na.rm=T)]) %>%
    select(group, Before, After) %>%
    mutate(
      Diff = After - Before
    ) 
  DnD <-
    rbind(
      DnD,
      data.frame(group='Effect - 72 Hours',Before=NA,After=NA,Diff=DnD[group=='72 Hours',Diff]-DnD[group=='Control',Diff]),
      data.frame(group='Effect - 4-8 Weeks',Before=NA,After=NA,Diff=DnD[group=='4-8 Weeks',Diff]-DnD[group=='Control',Diff])
    )
  
  DnD[,
      ':='(
        Before = percent(Before), After = percent(After), Diff = percent(Diff))
      ][grepl('Effect', group),
        ':='(
          Before = NA,
          After = NA
        )
      ]
  
}

textDrive.DnD <- DnD(ctd, 'textDrive.yn') %>% kable(digits = 4, align = 'l') %>% print()
```


3. Effectiveness is most prominent amongst licensed drivers, and may actually be detrimental in non-licensed drivers
    a) This is determined by observing the distirebution in outcomes ac ross the 3 groups. We can see that licensed drivers responded the most and in the expected direction. Permitted drivers are less responsive and go in the opposite direction as what is expected, but have a very high base rate of almost never texting and driving. The same seems to be the case for inidividuals who were neither permitted nor licensed

```{r, message=FALSE, warning=FALSE, echo=FALSE}
proportionPivot <- function(data, pivot=NULL) {
  if(is.null(pivot)) { 
    outcomeFreq <-
      ctd %>%
      as_tibble() %>%
      filter(textDrive != "I don't drive") %>%
      group_by_('textDrive', 'group') %>%
      summarise(
        count = n()
      ) %>%
      left_join(
        ctd %>% as_tibble %>% filter(textDrive != "I don't drive") %>% group_by_('group') %>% summarise(countGroup = n())
      ) %>%
      mutate(
        proportion = count / countGroup
      ) %>%
      tbl_dt()
  } else {
    outcomeFreq <-
      ctd %>%
      as_tibble() %>%
      filter(textDrive != "I don't drive") %>%
      group_by_('textDrive', 'group', pivot) %>%
      summarise(
        count = n()
      ) %>%
      left_join(
        ctd %>% as_tibble %>% filter(textDrive != "I don't drive") %>% group_by_('group', pivot) %>% summarise(countGroup = n())
      ) %>%
      mutate(
        proportion = count / countGroup
      ) %>%
      tbl_dt()
  }
  
  return(outcomeFreq)
  
}

proportionPlot <- function(data, wrap, title) {
  plot <- ggplot(data, aes(x=group, y=proportion, group=textDrive)) +
    geom_bar(stat='identity',position='stack',aes(fill=textDrive)) + facet_wrap(~get(wrap)) +
    scale_y_continuous(breaks = pretty_breaks(n=10)) +
    theme(plot.title = element_text(hjust = 0.5)) + ggtitle(paste(title))
  return(plot)
}

overallPlot <- 
  ggplot(proportionPivot(ctd), aes(x=group,y=proportion,group=textDrive)) +
  geom_bar(stat='identity',position='stack',aes(fill=textDrive)) +
  scale_y_continuous(breaks = pretty_breaks(n=10)) +
  theme(plot.title = element_text(hjust = 0.5)) + ggtitle('Overall')

proportionsLicenseType <- 
  proportionPivot(ctd, 'licenseType') %>%
  proportionPlot('licenseType', 'License Type') %>%
  print()

proportionsGender <- 
  proportionPivot(ctd, 'gender') %>%
  proportionPlot('gender', 'Gender') 
```

4. Daily drivers appear to be the most responsive
    a) Individuals who drive daily or monthly show the same pattern as the aggregate. 
    b) Weekly drivers do not respond as expected

```{r, message=FALSE, warning=FALSE, echo=FALSE}
proportionsDriveFrequncy <- 
  proportionPivot(ctd, 'driveFrequency') %>%
  proportionPlot('driveFrequency', 'Drive Frequency') %>%
  print()

proportionsGeography <- 
  proportionPivot(ctd, 'geography') %>%
  proportionPlot('geography', 'Geography') 

control <- rpart(
  as.factor(textDrive.yn) ~ 
    gender + geography + driveFrequency + licenseType, 
  data = ctd[group=='Control' & !is.na(textDrive.yn)]
  , cp=0.01)

exp <- rpart(
  as.factor(textDrive.yn) ~ 
    group + gender + geography + driveFrequency + licenseType, 
  data = ctd[group!='Control']
  , cp=0.01) 

#controlPlot <- rpart.plot(control, main="Control")
#expPlot <- rpart.plot(exp, main='Experiment')
```

5. Other charcateristics captured in the survey do not seem to be important drivers of likelihood to text and drive

```{r, message=FALSE, warning=FALSE, echo=FALSE}
ctrl = trainControl(method="repeatedcv", number=10, repeats=2, selectionFunction = "oneSE", 
                    classProb=T, summaryFunction = twoClassSummary, savePredictions = TRUE)

ctd %<>% mutate(textDrive.rf = as.factor(ifelse(textDrive.yn == 1, 'yes', 'no')))

candidates = c('gender', 'geography', 'driveFrequency', 'licenseType', 'group')
formula = as.formula(paste('textDrive.rf ~ ',paste(candidates, sep = ' + ', collapse = '+')))

rf = train(
  formula, 
  data=ctd[!is.na(textDrive.yn)], 
  method="rf", 
  metric="ROC",
  trControl=ctrl
)

varImp(rf, scale=FALSE) %>% plot(main = 'Variable Importance via Random Forest')
```

6. With the key drivers identified, we can estimate their relative impact on likelihood to text and drive. The size of the changes in behavior are visually represented below as changes in likelihood to text and drive across the 3 survey groups. This suggests that our greatest impact is on the licensed population that drives either Daily or Weekly. 

```{r, , message=FALSE, warning=FALSE, echo=FALSE}

remainingCandidates <- c('geography', 'driveFrequency', 'licenseType', 'group')
formula = as.formula(paste('textDrive.yn ~ ',paste(remainingCandidates, sep = ' + ', collapse = '+')))

linMod <- glm(formula, 'binomial', data = ctd[!is.na(textDrive.yn)])

finalCandidates <- c('driveFrequency', 'licenseType', 'group')
formula = as.formula(paste('textDrive.yn ~ ',paste(finalCandidates, sep = ' + ', collapse = '+'), '+ group*licenseType'))

linMod <- glm(formula, 'binomial', data = ctd[!is.na(textDrive.yn)])

effects <- 
  data.table(
  Name = names(coef(summary(linMod))[,1]), 
  Coef = coef(summary(linMod))[,1], 
  SE = coef(summary(linMod))[,2],
  pVal = round(coef(summary(linMod))[,4], 4)
  ) %>%
  tbl_dt() %>%
  filter(Name != '(Intercept)') %>%
  mutate(
    effectSize = logit2prob(Coef)
  )

Probs <- 
  expand.grid(
    driveFrequency = unique(ctd[!is.na(textDrive.yn), driveFrequency]),
    licenseType = unique(ctd[!is.na(textDrive.yn), licenseType]),
    group = unique(ctd[!is.na(textDrive.yn), group])
  ) %>%
  tbl_dt()
Probs %<>% mutate(pTextDrive = predict(linMod, Probs, type='response'))

ggplot(Probs[licenseType != 'Neither'], aes(x=driveFrequency, y=pTextDrive, group=group)) + 
  geom_bar(stat='identity', position='dodge', aes(fill=group)) + 
  facet_wrap(~licenseType) + scale_y_continuous(breaks = pretty_breaks(n=20)) +
  labs(x='Driving Frequency', y='Likelihood to Text & Drive', title='Campaign Effectiveness - Effect Size in Likelihood to Text & Drive') + 
  theme(plot.title = element_text(hjust = 0.5))

probTable <- 
  Probs %>%
  spread(
    group, pTextDrive
  ) %>%
  kable(align = 'l', digits = 4) 

```

#####Future Iterations

We see several potential improvements for future versions of the survey.

1. It would be very useful to either more robustly capture e-mail addresses, or capture phone numbers from survey takers. This would allow us to link individuals with the rest of our data, drastically broadening the scope of feature exploration. 
2. We should try to maintain a consistent stream of surveys throughout the campaign. This would provide a better estimate of exogenous activity driving changes in texting and driving behavior