---
title: "Monthly MAM Report"
output: html_notebook
---

* Summary
    - MAM has decreased significantly in the past 2 months
    - Seasonality can no longer be blamed as last May was a strong month
    - Biggest driver appears to be a drop in messages received by gambit
    - Top of the funnel supplemental analysis shows that:
        - **SMS** conversion is consistent; we have somply messaged less the past two months and saw especially strong engagement in March
        - **Email**'s contribution has worsened with a similar number of messages leading the fewer clicks
        - **Web** traffic has increased and has been coupled with increases in activity, so is not a driver
            - Most marketing partners have actually increased the amount of traffic they are sending

#### Deeper Dive
* Overall Trend
    * This is the third consecutive month MAM has decreased
    * Last May was a good month, so seasonality is not the issue
```{r warning=FALSE, echo=FALSE, fig.width=10, fig.height=6.5}
labs <- mm %>% group_by(Month) %>% summarise(count=sum(nsids))
ggplot(mm %>% filter(Month<'2018-06-01'), aes(x=as.factor(Month), y=nsids)) + 
  geom_bar(stat='identity') + 
  labs(title='Overall Trend', y='Distinct Users', x='Month') + 
  stat_summary(fun.y = sum, aes(label = ..y.., group = Month), geom = "text", vjust=-.2) +
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  theme(plot.title=element_text(hjust=.5),
        axis.text.x = element_text(angle = 30, hjust = 1)) 
```

* Action Types
	  * Activity decreased across all action types
	  * Biggest drops in the past 2 months have been in messages sent to gambit and corresponding signups - this is the smallest number of recorded messages to gambit
	  * This appears to be the biggest driver of the decrease in MAM
	  * One positive is that the number of reportbacks continues to increase
	  * Email link clicks are less than half of thier peak 2 months ago
	  * Web activity is fairly consistent
* Activity composition 
    * Historically, activity composition has been fairly consistent even while MAM fluctuates
    * Decreased contribution from Email and SMS is prominent
	
```{r warning=FALSE, echo=FALSE, fig.width=12, fig.height=6.5}
act.agg <- act %>% group_by(Month, action_type) %>% summarise(count = sum(actions))
ggplot(act.agg %>% filter(Month<'2018-06-01'), aes(x=as.factor(Month), y=count, fill=reorder(action_type, count))) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust=.5), aes(label=count), vjust=0, size=2.5) +
  stat_summary(fun.y = sum, aes(label = ..y.., group = Month), geom = "text", vjust=-.4) +
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  labs(title='Action Counts', y='Actions', x='Month') + 
  theme(plot.title=element_text(hjust=.5),
        axis.text.x = element_text(angle = 30, hjust = 1)) + 
  guides(fill=guide_legend(title="Action Type")) +
  scale_fill_brewer(palette="Set3")

ggplot(act.N %>% filter(Month<'2018-06-01'), aes(x=as.factor(Month), y=prop, fill=reorder(action_type, prop))) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust=.5), aes(label=Text), size=2.5) +
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  theme(plot.title=element_text(hjust=.5),
        axis.text.x = element_text(angle = 30, hjust = 1)) + 
  labs(y='Proportion', x='Month', title='Action Composition') +
  guides(fill=guide_legend(title="Action Type")) +
  scale_fill_brewer(palette="Set3")
```

* Action Taken Per Member
    * Across member type and source, the average number of actions taken per member is steadily ascending
    * Among new members, the numbers are fairly comparable in the previous months, though the trend among returning is still positive
```{r warning=FALSE, echo=FALSE, fig.width=12, fig.height=6.5}
ggplot(filter(actMemAvg %>% filter(Month<'2018-06-01')), aes(x=Month, y=avg_n_actions, color=Type)) +
  geom_line() + geom_point() + facet_wrap(~niche) +
  scale_x_date(breaks=pretty_breaks(20)) + 
  labs(title='Average # of Actions Taken Per Member', y='# of Actions', x='Month') + 
  theme(
    plot.title=element_text(hjust=.5),
    axis.text.x = element_text(angle = 30, hjust = 1)
    )
```
* Getting back to MAM
    * Breaking out by Niche/Non-Niche will become increasinly pointless as niche is pointed straight to the website, and so, is treated like any other user. 
    * Drop in member activity over past 2 months is consistent across member types
    * Next step here is start breaking out by channel (this information is available in tabular form in the deep dive document)
```{r warning=FALSE, echo=FALSE, fig.width=12, fig.height=6.5}
ggplot(mm %>% filter(Month<'2018-06-01'), aes(x=as.factor(Month), y=nsids, fill=Type)) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust = 0.5), aes(label=nsids), size=2.5) +
  stat_summary(fun.y = sum, aes(label = ..y.., group = Month), geom = "text", vjust=-.4, size=3) +
  facet_wrap(~niche) + 
  labs(y='Distinct Users', x='Month') + 
  scale_y_continuous(breaks=pretty_breaks(16)) +
  scale_fill_brewer(palette="Set2") + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

* Unique users per day over time, split by day of week
    * May was seriously lacking in big days; there was only 1 day where we accumulated 20k unique members
    * Next step is to pivot this out by SMS/Web
```{r warning=FALSE, echo=FALSE, message=FALSE, fig.width=12, fig.height=6.5}
ggplot(filter(da, active_members != max(active_members)), aes(x=date, y=active_members)) +
  geom_point(aes(colour=DayOfWeek), size=.8) +
  geom_smooth(method='loess',se=F, aes(colour=DayOfWeek)) +
  scale_x_date(breaks=pretty_breaks(16)) +
  theme(plot.title=element_text(hjust=.5),
        axis.text.x = element_text(angle = 30, hjust = 1)) +
  # scale_colour_brewer(palette='Spectral') +
  labs(title='Users Per Day Over Time', x='Date', y='Active Members')
```

* Time on Site
    * Web engagement is trending up, but is largely still a random walk
    * Web NPS is at 38 now, suggesting that the web experience is consistently getting better
```{r warning=FALSE, echo=FALSE, fig.width=10, fig.height=6.5}
ggplot(tos, aes(x=date, y=avgTimeOnSite)) + 
  geom_line() + geom_smooth(method='loess',se=F, linetype='dotdash', color='blue') + 
  scale_x_date(breaks=pretty_breaks(10)) +
  labs(x='Day', y='Minutes Spent On Site') + 
  theme(plot.title=element_text(hjust=.5))
```