---
title: "Monthly MAM Report"
output: html_notebook
---


#### Deeper Dive

* We see an increase from Feb but not as much as last year
```{r warning=FALSE, echo=FALSE, fig.width=11, fig.height=6.5}
labs <- mm %>% group_by(month) %>% summarise(count=sum(count))
ggplot(mm, aes(x=month, y=count)) + 
  geom_bar(stat='identity') + 
  ggtitle('Overall Trend') + 
  geom_text(data = labs, aes(x=month, label=count, y=count), vjust=-1, size=2.5) + 
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  theme(plot.title=element_text(hjust=.5)) 
```
* Pivoting by Niche and New/Returning
	* Niche overall active looks comparable to last year
	  * A 3:1 new:repeat ratio in niche has given way to roughly 45:55 ratio
	* Most of the decline appears to be among non-niche, occuring in both new and repeat
	  * Ratio of new:repeat is not very different
```{r warning=FALSE, echo=FALSE, fig.width=18, fig.height=6.5}
ggplot(mm, aes(x=month, y=count, fill=return_user)) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust = 0.5), aes(label=count), size=2.5) +
  stat_summary(fun.y = sumIf, aes(label = ..y.., group = month), geom = "text", vjust=-.2) +
  facet_wrap(~niche) + 
  scale_y_continuous(breaks=pretty_breaks(16)) +
  scale_fill_brewer(palette="Set2")
```
* Pivoting by Action Types
	* Very interesting that the total number of actions taken is actually a bit higher than last year
	* This suggests we have fewer people taking more actions
	* Account creations are down but website utilization is up
```{r warning=FALSE, echo=FALSE, fig.width=16, fig.height=6.5}
act.agg <- act %>% group_by(month, action_type) %>% summarise(count = sum(count))
ggplot(act.agg, aes(x=month, y=count, fill=reorder(action_type, count))) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust=.5), aes(label=count), vjust=0, size=2.5) +
  stat_summary(fun.y = sumIf, aes(label = ..y.., group = month), geom = "text", vjust=-.2) +
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  ggtitle('Action Counts') + 
  theme(plot.title=element_text(hjust=.5)) + 
  guides(fill=guide_legend(title="Action Type")) +
  scale_fill_brewer(palette="Set2")
```
* Splitting by Niche
  * Both niche and non-niche show the same pattern of slightly more activity this March
  * Similar action type breakdowns as overall with fewer new accounts, but more site activity
```{r warning=FALSE, echo=FALSE, fig.width=18, fig.height=6.5}
ggplot(act, aes(x=month, y=count, fill=reorder(action_type, count))) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust = 0.5), aes(label=count), vjust=0, size=2.5) +
  stat_summary(fun.y = sumIf, aes(label = ..y.., group = month), geom = "text", vjust=-.3) +
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  ggtitle('Action Counts') + facet_wrap(~niche) + 
  theme(plot.title=element_text(hjust=.5)) + 
  guides(fill=guide_legend(title="Action Type")) +
  scale_fill_brewer(palette="Set2")
```
* Activity composition 
  * Activity breakdown delta shows up even more clearly here; lots more website activity
```{r warning=FALSE, echo=FALSE, fig.width=16, fig.height=6.5}
ggplot(act.N, aes(x=month, y=prop, fill=reorder(action_type, prop))) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust=.5), aes(label=Text), size=2.5) +
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  theme(plot.title=element_text(hjust=.5)) + 
  labs(y='Proportion', title='Action Composition') +
  guides(fill=guide_legend(title="Action Type")) +
  scale_fill_brewer(palette="Set2")
```
* Splitting by Niche
  * Same story holds when breaking out niche and non-niche
```{r warning=FALSE, echo=FALSE, fig.width=18, fig.height=6.5}
ggplot(act, aes(x=month, y=prop, fill=reorder(action_type, prop))) + 
  geom_bar(stat='identity', position='stack') + 
  geom_text(position=position_stack(vjust=.5), aes(label=Text), size=3) +
  facet_wrap(~niche) + 
  scale_y_continuous(breaks=pretty_breaks(10)) + 
  labs(title='Action Composition', y='Proportion') + 
  theme(plot.title=element_text(hjust=.5)) +
  guides(fill=guide_legend(title="Action Type")) +
  scale_fill_brewer(palette="Set2")
```


