---
title: "Brake It Down Survey Analyses"
output: html_notebook
---

```{r, include = FALSE}
library(gmodels)
library(glue)
library(tidyverse)
library(reshape2)
library(scales)
library(ggpubr)
```


```{r, include = FALSE}
#############################################################
################ QUIZ DATA #######################
#############################################################

#Pull Quiz data
bid_quiz <- ("SELECT 
             e.records #>> '{_id,$oid}' AS event_id,
             to_timestamp((e.records #>> '{meta,timestamp}')::bigint/1000) AS meta_timestamp,
             e.records #>> '{user,northstarId}' AS northstar_id,
             e.records #>> '{page,path}' AS url,
             e.records #> '{data,responses}' ->> '0' AS response_1,
             e.records #> '{data,responses}' ->> '1' AS response_2,
             e.records #> '{data,responses}' ->> '2' AS response_3,
             e.records #> '{data,responses}' ->> '3' AS response_4
             FROM puck.events_json e
             WHERE e.records #>> '{data,responses}' IS NOT NULL 
             AND e.records #>> '{page,path}' ILIKE '%brake%'")

bid_quiz<- runQuery(bid_quiz)

#remove dups if they retook the quiz
bid_quiz <- bid_quiz%>%
  filter(!duplicated(northstar_id))

#Only look at those with url best-friend or sms
bid_quiz <- bid_quiz%>%
  filter((url=='/us/campaigns/brake-it-down/quiz/best-friend'| url=='/us/campaigns/brake-it-down/quiz/best-friend-sms'))%>%
  mutate(group = 
           case_when(response_4=='0' ~ 'Driving',
                     response_4=='1' ~ 'Riding in the Passenger Seat',
                     response_4=='2'|response_4=='3' ~ 'Riding a Bike/Walking'),
         car =
           case_when(response_1=='0' ~ 'Electric Car',
                     response_1=='1' ~ 'Pickup truck',
                     response_1=='2' ~ 'Convertible',
                     response_1=='3' ~ 'SUV'),
        snack =
            case_when(response_2=='0' ~ 'Chips',
                      response_2=='1' ~ 'Cookies',
                      response_2=='2' ~ 'Fruit',
                      response_2=='3' ~ 'Candy'),
        dj =
            case_when(response_3=='0' ~ 'Drake',
                      response_3=='1' ~ 'Ed Sheeran',
                      response_3=='2' ~ 'Taylor Swift',
                      response_3=='3' ~ 'Beyonce'))
```

#BID ONLINE QUIZ#

####Most quiz takers said their friends were Drivers (59%)####

```{r, include = FALSE}
#Percentages of friends are drivers/passengers/pedestrians from BID quiz
driver_type <- count(bid_quiz, group, sort = TRUE)%>%
  filter(group!="")%>%
  mutate(pct=round(n/sum(n)*100,2))

# Create a basic bar
driver = ggplot(driver_type, aes(x="", y=pct, fill=group)) + 
          geom_bar(stat="identity", width=1) +
          coord_polar("y", start=0) + 
          geom_text(aes(label = paste0(round(pct), "%")), position = position_stack(vjust = 0.5)) +
          labs(x = NULL, y = NULL, fill = NULL, title = "How is your friend most likely to get around?") +
          theme_classic() +
          theme(axis.line = element_blank(),
            axis.text = element_blank(),
            axis.ticks = element_blank(),
            plot.title = element_text(hjust = 0.5, color = "#666666"))
```
```{r}
driver
```

```{r, include=FALSE}
# Percent of car preference
car_type <- count(bid_quiz, car, sort = TRUE)%>%
  filter(car!="")%>%
  mutate(pct=round(n/sum(n)*100,2))

# Create chart
car = ggplot(car_type, aes(x="", y=pct, fill=car)) + 
        geom_bar(stat="identity", width=1) +
        coord_polar("y", start=0) + geom_text(aes(label = paste0(round(pct), "%")), position = position_stack(vjust = 0.5)) +
        labs(x = NULL, y = NULL, fill = NULL, title = "Which would your friend most like to drive?") +
        theme_classic() +
        scale_fill_brewer(type = "qual", palette = "Dark2") +
        theme(axis.line = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5, color = "#666666"))
```

####35% said their friend would want to drive a convertible, 30% said an electric car####

```{r}
car
```


```{r, include = FALSE}
#Pull Phoenix Next Data to look at counts of views for each guide
guide_types <- sql("SELECT 
                      COUNT(DISTINCT (CASE WHEN pe.href LIKE '%road-safety-guide-daredevil%'
                	      then pe.event_id else NULL end)) AS Daredevil,
                	    COUNT(DISTINCT (case when pe.href LIKE '%road-safety-guide-jaywalker%'
                	      then pe.event_id else NULL end)) AS Jaywalker,
                	    COUNT(DISTINCT (case when pe.href LIKE '%road-safety-guide-cell%'
                	      then pe.event_id else NULL end)) AS Cell,
                	    COUNT(DISTINCT (case when pe.href LIKE '%road-safety-guide-chatty%'
                	      then pe.event_id else NULL end)) AS Chatty_Cathy,
                	    COUNT(DISTINCT (case when pe.href LIKE '%road-safety-guide-impatient%'
                	      then pe.event_id else NULL end)) AS Impatient,
                	    COUNT(DISTINCT (case when pe.href LIKE '%road-safety-guide-late%'
                	      then pe.event_id else NULL end)) AS Late,
                	    COUNT(DISTINCT (case when pe.href LIKE '%road-safety-guide-karaoke%'
                	      then pe.event_id else NULL end)) AS Karaoke
                	  FROM public.phoenix_events pe
                	  WHERE pe.event_name = 'view'")

guide_types <-runQuery(guide_types)

#reshape from wide to long
guide_total <-melt(guide_types)

```

####The most popularly viewed guides were the Late and Impatient guides (followed by the Karaoke)####

```{r, include = FALSE}
#calculate pct
guide_total <- guide_total%>%
                rename(Guide=variable)%>%
                mutate(total=as.numeric(sum(value)),
                       pct=(value/total)*100,
                       Guide=
                         case_when(
                           Guide=='daredevil' ~ 'Daredevil',
                           Guide=='jaywalker' ~ 'Jaywalker',
                           Guide=='cell' ~ 'Cell Phone Stroller',
                           Guide=='chatty_cathy' ~ 'Chatty Cathy',
                           Guide=='impatient' ~ 'Impatient Player',
                           Guide=='late' ~ 'Late Date',
                           Guide=='karaoke' ~ 'Karaoke')
                              )%>%
                select(-value,-total)

# Create pie chart
pie = ggplot(guide_total, aes(x="", y=pct, fill=Guide)) + 
      geom_bar(stat="identity", width=1) +
      # Convert to pie (polar coordinates) and add labels
      coord_polar("y", start=0) + geom_text(aes(label = paste0(round(pct), "%")), position = position_stack(vjust = 0.5)) +
      # Remove labels and add title
      labs(x = NULL, y = NULL, fill = NULL, title = "Break It Down Guides Viewed") +
      # Tidy up the theme
      theme_classic() + theme(axis.line = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          plot.title = element_text(hjust = 0.5, color = "#666666"))
```

```{r}
print(pie)
```


#BRAKE IT DOWN SURVEY DATA#

```{r, include = FALSE}
################## TYPEFORM DATA ############################
## Upload experiment/control surveys and rename columns

#Upload Typeform Brake It Down responses 
bid_typeform <- read.csv('~/Documents/Brake it Down/Brake It Down Oct 9.csv', na.strings=c("", "NA"))
bid_typeform$group = "experiment"

#Rename columns
desiredColnames <- c('X.', 
                     'age', 
                     'gender', 
                     'gender_other', 
                     'region', 
                     'zipcode', 
                     'mode_transportation', 
                     'perceived_speeding', 
                     'feeling_nervous', 
                     'feeling_indifferent', 
                     'feeling_exhilarated', 
                     'feeling_annoyed', 
                     'feeling_dont_notice', 
                     'speeding_reason_other', 
                     'speeding_reason', 
                     'Other.2', 
                     'speeding_freq_highways', 
                     'speeding_freq_residential', 
                     'danger', 
                     'perception_reduces_crash', 
                     'perception_5mph_acceptable', 
                     'perception_15mph_notacceptable', 
                     'intervention', 
                     'witnessed', 
                     'attempted_intervention', 
                     'intervened_asked', 
                     'intervened_stats', 
                     'intervened_jokes', 
                     'intervened_honked', 
                     'intervened_shouted', 
                     'intervened_other', 
                     'read_guide', 
                     'thought_differently', 
                     'thought_differently_how', 
                     'email', 
                     'id', 
                     'source', 
                     'Start.Date..UTC.', 
                     'Submit.Date..UTC.', 
                     'Network.ID',
                     'group')

#Set names 
for (i in 1:length(colnames(bid_typeform))) {
  colnames(bid_typeform)[i] <- desiredColnames[i]
}

#remove duplicate emails, irrelevant vars and only select members who read the BID guide
bid_typeform_nodup <-bid_typeform%>%
  filter(!duplicated(email) & read_guide==1)%>%
  select(-id, -source, -Network.ID, -X.)

############### CONTROL SURVEY ######################
#Upload Control survey data
bid_control <-read.csv('~/Documents/Brake it Down/Brake it Down Control Oct 9.csv', na.strings=c("", "NA"))
bid_control$group = "control"

#Rename columns
desiredColnames_control <- c('X.', 
                             'age', 
                             'gender', 
                             'gender_other', 
                             'region', 
                             'zipcode', 
                             'mode_transportation', 
                             'perceived_speeding', 
                             'feeling_nervous', 
                             'feeling_indifferent', 
                             'feeling_exhilarated', 
                             'feeling_annoyed', 
                             'feeling_dont_notice', 
                             'speeding_reason_other', 
                             'speeding_reason', 
                             'Other.2', 
                             'speeding_freq_highways', 
                             'speeding_freq_residential', 
                             'danger', 
                             'perception_reduces_crash', 
                             'perception_5mph_acceptable', 
                             'perception_15mph_notacceptable', 
                             'intervention', 
                             'witnessed', 
                             'attempted_intervention', 
                             'intervened_asked', 
                             'intervened_stats', 
                             'intervened_jokes', 
                             'intervened_honked', 
                             'intervened_shouted', 
                             'intervened_other', 
                             'northstar_id', 
                             'Start.Date..UTC.', 
                             'Submit.Date..UTC.', 
                             'Network.ID',
                             'group')

#Set names for control
for (i in 1:length(colnames(bid_control))) {
  colnames(bid_control)[i] <- desiredColnames_control[i]
}

#remove dups and irrelevant vars
bid_control_nodup <- bid_control%>%
  filter(!duplicated(northstar_id))%>%
  select(-X., -Network.ID)
```

```{r, include = FALSE}
#Combine Control and Experiment surveys 
all_bid_readguide <- bind_rows(bid_control_nodup,bid_typeform_nodup)

#Create new variables
all_bid_readguide <-all_bid_readguide %>%
  mutate_at(vars(starts_with('perception')), function(x) as.numeric(substr(x, 1, 1)))%>%
  mutate_at(vars(starts_with('feeling')), .funs = funs(ifelse(is.na(.), 0, 1)))%>%
  mutate_at(vars(starts_with('intervened')), .funs = funs(ifelse(is.na(.), 0, 1)))%>%
  mutate(survey_submit = as.Date(as.numeric(as.Date(substr(Submit.Date..UTC., 1, 10))), origin='1970-01-01'),
           gender = 
             case_when(
               gender == 'Woman' ~ 'Female',
               gender == 'Man' ~ 'Male',
               TRUE ~ 'Other'),
           age =
            case_when(
               age == 'Older than 25' ~ '26',
               age == 'Younger than 15' ~ '14',
               TRUE ~ as.character(age)),
           age_numeric = as.numeric(age),
           attempted_intervention_dummy = 
             case_when(
               attempted_intervention == 'No, I did not try to convince them to slow down' ~ 'No',
               attempted_intervention == 'Yes, I tried to convince them to slow down' ~ 'Yes'),
            speeding_freq_highways_numeric = 
             case_when(
               speeding_freq_highways == 'Never' ~ 0,
               speeding_freq_highways == 'Rarely' ~ .33,
               speeding_freq_highways == 'Sometimes' ~ .66,
               speeding_freq_highways == 'Often' ~ 1,
               speeding_freq_highways %in% 'I don' ~ NA_real_,
               speeding_freq_highways = is.na(speeding_freq_highways) ~ NA_real_),
            witnessed_speeding = 
             case_when(
               witnessed == 'No, as far as I know everyone drove the speed limit' ~ 'No',
               witnessed == 'Yes, I saw someone speeding' ~ 'Yes'),
            transportation = 
             case_when(
               mode_transportation == 'Driving' ~ 'Driver',
               mode_transportation == 'Riding in the passenger seat' ~ 'Passenger',
               TRUE ~ 'Pedestrian'),
            speeding_freq_residential_numeric = 
             case_when(
               speeding_freq_residential == 'Never' ~ 0,
               speeding_freq_residential == 'Rarely' ~ .33,
               speeding_freq_residential == 'Sometimes' ~ .66,
               speeding_freq_residential == 'Often' ~ 1,
               speeding_freq_residential %in% 'I don' ~ NA_real_,
               speeding_freq_residential = is.na(speeding_freq_residential) ~ NA_real_)
    )
```

###_How are you most likely to get around?_###
####54% of respondents were Drivers####

```{r}
count(all_bid_readguide, mode_transportation, sort = TRUE)%>% mutate(pct=round(n/sum(n)*100,2))
```

    
###_What would be your main motivation for speeding?_###

####49% of respondents said they would speed to get where they're going faster####


```{r}
#Reasons for speeding
count(all_bid_readguide, speeding_reason, sort = TRUE)%>% filter(speeding_reason!=is.na(speeding_reason))%>%mutate(pct=round(n/sum(n)*100,2))

```

###_How do you feel when you witness friends or family speeding? _###

#### The majority of respondents (70%) said they felt nervous ####
    
```{r, include=FALSE}
#only look at feelings
feelings <- all_bid_readguide%>%
  select(starts_with('feeling'))
#Calculate sum of 1s for each feeling dummy variable
feelings_ct <- colSums(feelings)
#reshape from short to long
feelings_ct <-melt(feelings_ct)%>%
             select(value)

#Grab column names and reshape to long
feelings_names <-colnames(feelings)
feelings_names <- melt(feelings_names)%>%
                 rename(feeling=value)

#combine column names and totals and add pct
feelings_merged <-cbind(feelings_ct,feelings_names)%>%
  mutate(pct=round(value/nrow(feelings),4),
         feeling=
           case_when(
             feeling == 'feeling_nervous' ~ 'Nervous',
             feeling == 'feeling_indifferent' ~ 'Indifferent',
             feeling == 'feeling_exhilarated' ~ 'Exhilarated',
             feeling == 'feeling_annoyed' ~ 'Annoyed',
             feeling == 'feeling_dont_notice' ~ 'Dont Notice')
           )

```

```{r, include=FALSE}
#Bar chart
feelings_chart <- ggplot(feelings_merged, aes(x=feeling, y=pct)) + 
                        geom_bar(stat="identity", width= 0.75, position = "dodge", fill="#FF6666") +
                        geom_text(aes(label=scales::percent(pct)), 
                                  vjust=-1, position =position_dodge(width=0.9),  size=3) + 
                        ylab('Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                                           limits = c(0, .80)) + 
                        theme(axis.text.x = element_text(angle = 15, hjust = 1), 
                              legend.position="top", legend.title=element_blank(),
                              axis.title.x=element_blank(),
                              axis.title.y=element_blank()) + 
                        ggtitle("How do you feel when you witness friends or family speeding??") +
                        scale_fill_manual(values=c('#000000',"#23b7fbff"))
```

```{r}
feelings_chart
```

    
```{r, include=FALSE}
#quickly check counts/pcts match chart 
# count(all_bid_readguide, feeling_annoyed)%>% mutate(pct=round(n/sum(n)*100,2))
# count(all_bid_readguide, feeling_nervous)%>% mutate(pct=round(n/sum(n)*100,2))
# count(all_bid_readguide, feeling_indifferent)%>% mutate(pct=round(n/sum(n)*100,2))
# count(all_bid_readguide, feeling_exhilarated)%>% mutate(pct=round(n/sum(n)*100,2))
# count(all_bid_readguide, feeling_dont_notice)%>% mutate(pct=round(n/sum(n)*100,2))
```

###Speeding Frequency###

####We saw no statistically significant change in speeding behavior between the control and experiment groups (p>0.05) ####

```{r, include = FALSE}
freq_highway <- all_bid_readguide%>%
  group_by(group)%>%
  filter(!is.na(speeding_freq_highways_numeric) & !is.na(speeding_freq_highways))%>%
  count(speeding_freq_highways, sort=TRUE)%>%
  mutate(pct=round(n/sum(n),4),
         speeding_freq_highways=
           factor(speeding_freq_highways,c("Never", "Rarely", "Sometimes", "Often")))

freq_residential <- all_bid_readguide%>%
  group_by(group)%>%
  filter(!is.na(speeding_freq_residential_numeric) & !is.na(speeding_freq_residential))%>%
  count(speeding_freq_residential, sort=TRUE)%>%
  mutate(pct=round(n/sum(n),4),
         speeding_freq_residential=
           factor(speeding_freq_residential,c("Never", "Rarely", "Sometimes", "Often")))
```

```{r, include = FALSE}
#Bar charts
speed_highway_chart <- ggplot(freq_highway, aes(x=speeding_freq_highways, y=pct, group = group, fill=group)) + 
                        geom_bar(stat="identity", position = "dodge", colour="grey") +
                        geom_text(aes(label=scales::percent(pct)), vjust=-1, position = position_dodge(width=0.9),  size=3) + 
                        labs(x = 'Frequency', y = 'Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 0.45)) + 
                        theme(axis.text.x = element_text(angle = 20, hjust = 1), legend.position="top", 
                              legend.title=element_blank(),
                              axis.title.x=element_blank(),
                              axis.title.y=element_blank()) + 
                        ggtitle("How often do you drive 15 miles an hour over the speed limit on highways?") +
                        scale_fill_manual(values=c('#000000',"#23b7fbff"))
```

```{r}
print(speed_highway_chart)
```

```{r, include = FALSE}
speed_res_chart <- ggplot(freq_residential, aes(x=speeding_freq_residential, y=pct, group = group, fill=group)) + 
                    geom_bar(stat="identity", position = "dodge", colour="grey") +
                    geom_text(aes(label=scales::percent(pct)), vjust=-1, position = position_dodge(width=0.9),  size=3) + 
                    labs(title = "How often do you drive 10 miles an hour over the speed limit on \n neighborhood/residential streets?",
                         x = 'Frequency', 
                         y = 'Percentage') + 
                    scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 0.45)) + 
                    theme(axis.text.x = element_text(angle = 20, hjust = 1), legend.position="top", 
                          legend.title=element_blank(), plot.title = element_text(hjust = 0.5),
                          axis.title.x=element_blank(),
                          axis.title.y=element_blank()) + 
                    scale_fill_manual(values=c('#000000',"#23b7fbff"))
```

```{r}
print(speed_res_chart)
```

```{r, include=FALSE}
#chi-square test to test significance of group differences
test_highway <- all_bid_readguide%>%
                filter(!is.na(speeding_freq_highways_numeric) & !is.na(speeding_freq_highways))
CrossTable(test_highway$speeding_freq_highways, test_highway$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))

test_residential <- all_bid_readguide%>%
                filter(!is.na(speeding_freq_residential_numeric) & !is.na(speeding_freq_residential))
CrossTable(test_residential$speeding_freq_residential, test_residential$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))

```


###Perceptions###

    + Respondents were asked "How dangerous is it to speed?" (1=Not Very Dangerous, 5= Very Dangerous)
    
    + Respondents were also asked "How much do you agree with the following?"(1=Strongly disagree, 5= Strongly Agree)
        + It is unacceptable to exceed speed limits by more than 15mph 
        + It is socially acceptable to exceed speed limits by 5mph
        + Driving at or near the speed limit reduces my chances of a crash
        
####BID participants were more likely to agree that speeding is very dangerous and disagree that it is socially acceptable to drive over 5mpg than the control group (p<0.05)####


```{r, include = FALSE}
#Bar charts for perceptions
pivotBars <- function(expid='group', pivot=NULL, title=NULL) {
  if (is.null(pivot)) {
    all_bid_readguide %>% 
      group_by_(expid) %>% 
      summarise(
        `Driving at the speed limit reduces chances of crashing` = round(mean(perception_reduces_crash),2),
        `Socially acceptable to exceed speed limits by 5mph`= round(mean(perception_5mph_acceptable),2),
        `Unacceptable to exceed speed limits by more than 15mph` = round(mean(perception_15mph_notacceptable),2),
        `Speeding is very dangerous` = round(mean(danger),2)
      ) %>%
      melt(id.var=c(expid)) %>%
      ggplot(.,aes(x=variable, y=value, fill=get(expid))) +
      geom_bar(stat='identity', position='dodge') +
      geom_text(aes(label=round(value, 3)), position = position_dodge(width = 1), size=3, hjust=0) +
      coord_flip() + 
      ggtitle('Perceptions towards speeding') +
      theme(legend.position='bottom', 
            legend.title=element_blank(), 
            axis.title.y=element_blank(),
            axis.title.x=element_blank(),
            plot.title = element_text(hjust = 0.5),
            axis.text.y = element_text(face="bold", size=9)) +
      scale_fill_manual(values=c('#000000',"#23b7fbff"))
  } else {
    all_bid_readguide %>% 
      group_by_(expid, pivot) %>% 
      summarise(
        `Driving at the speed limit reduces chances of crashing` = mean(perception_reduces_crash),
        `Socially acceptable to exceed speed limits by 5mph`= mean(perception_5mph_acceptable),
        `Unacceptable to exceed speed limits by more than 15mph` = mean(perception_15mph_notacceptable),
        `Speeding is very dangerous` = mean(danger)
      ) %>%
      melt(id.var=c(expid,pivot)) %>%
      ggplot(.,aes(x=get(pivot), y=value, fill=get(expid))) +
      geom_bar(stat='identity', position='dodge') +
      geom_text(aes(label=round(value, 3)), vjust=-0.25, position = position_dodge(width = 1), size=2) +
      ggtitle(paste0('Pivoted by ',title)) +
      facet_wrap(~variable) + 
      theme(legend.position='none',
            axis.title.x=element_blank(), 
            axis.title.y=element_blank(),
            plot.title = element_text(hjust = 0.5),
            axis.text.x = element_text(face="bold", size=5),
            axis.text.y = element_text(face="bold", size=5),
            strip.text.x = element_text(size = 8)) +
      scale_fill_manual(values=c('#000000',"#23b7fbff"))
  }
}
```

```{r}
pivotBars(expid='group') %>% print()
```

```{r, include = FALSE}
#Test significance of perception means
t.test(all_bid_readguide$danger~all_bid_readguide$group)
t.test(all_bid_readguide$perception_reduces_crash~all_bid_readguide$group)
t.test(all_bid_readguide$perception_5mph_acceptable~all_bid_readguide$group)
t.test(all_bid_readguide$perception_15mph_notacceptable~all_bid_readguide$group)
```

####Participants from rural/suburban areas, drivers/passengers, and females were also more responsive on these two areas compared to other respective young people in the control group####

```{r}
# Perceptions pivoted by controls
controls <- c('region', 'transportation', 'gender')
titles <- c('Region', 'Transportation Type', 'Gender')
for (i in 1:length(controls)) {
  pivotBars(controls[i], titles[i],expid = 'group') %>% 
    print()
}
```

```{r, include=FALSE}
#T-tests for region##

#Rural
rural <- all_bid_readguide%>%
  filter(region == 'Rural')
#Check p<0.05
t.test(rural$danger~rural$group)
t.test(rural$perception_5mph_acceptable~rural$group)
#Check p>0.05
t.test(rural$perception_15mph_notacceptable~rural$group)
t.test(rural$perception_reduces_crash~rural$group)

#Suburban
suburban <- all_bid_readguide%>%
  filter(region == 'Suburban')
#Check p<0.05
t.test(suburban$danger~suburban$group)
t.test(suburban$perception_5mph_acceptable~suburban$group)
#Check p>0.05
t.test(suburban$perception_15mph_notacceptable~suburban$group)
t.test(suburban$perception_reduces_crash~suburban$group)

#Urban 
urban <- all_bid_readguide%>%
  filter(region == 'Urban')
#Check p>0.05 - no significance found
t.test(urban$danger~urban$group)
t.test(urban$perception_5mph_acceptable~urban$group)
t.test(urban$perception_15mph_notacceptable~urban$group)
t.test(urban$perception_reduces_crash~urban$group)

```

```{r, include=FALSE}
#T-tests for transportation type

#Driver
driver <- all_bid_readguide%>%
  filter(transportation == 'Driver')
#Check p<0.05
t.test(driver$danger~driver$group)
t.test(driver$perception_5mph_acceptable~driver$group)
#Check p>0.05
t.test(driver$perception_15mph_notacceptable~driver$group)
t.test(driver$perception_reduces_crash~driver$group)

#Passenger
passenger <- all_bid_readguide%>%
  filter(transportation == 'Passenger')
#Check p<0.05
t.test(passenger$danger~passenger$group)
t.test(passenger$perception_5mph_acceptable~passenger$group)
#Check p>0.05
t.test(passenger$perception_15mph_notacceptable~passenger$group)
t.test(passenger$perception_reduces_crash~passenger$group)

#Pedestrian
pedestrian<- all_bid_readguide%>%
  filter(transportation == 'Pedestrian')
#Check p<0.05
t.test(pedestrian$danger~pedestrian$group)
t.test(pedestrian$perception_5mph_acceptable~pedestrian$group)
#Check p>0.05
t.test(pedestrian$perception_15mph_notacceptable~pedestrian$group)
t.test(pedestrian$perception_reduces_crash~pedestrian$group)
```

```{r}
#Gender
male <- all_bid_readguide%>%
  filter(gender == 'Male')
#Check p>0.05
t.test(male$danger~male$group)
t.test(male$perception_5mph_acceptable~male$group)
t.test(male$perception_15mph_notacceptable~male$group)
t.test(male$perception_reduces_crash~male$group)

female <- all_bid_readguide%>%
  filter(gender == 'Female')
#Check p<0.05
t.test(female$danger~female$group)
t.test(female$perception_5mph_acceptable~female$group)
#Check p>0.05
t.test(female$perception_15mph_notacceptable~female$group)
t.test(female$perception_reduces_crash~female$group)
```



```{r, include=FALSE}
#Check for any differences in speeding behavior by region - None found 
# t.test(rural$speeding_freq_highways_numeric~rural$group)
# t.test(rural$speeding_freq_residential_numeric~rural$group)
# t.test(suburban$speeding_freq_highways_numeric~suburban$group)
# t.test(suburban$speeding_freq_residential_numeric~suburban$group)
# t.test(urban$speeding_freq_highways_numeric~urban$group)
# t.test(urban$speeding_freq_residential_numeric~urban$group)
```

###Younger respondents are more response on the outcome "It is socially acceptable to exceed limits by 5mph". They are more likely to disagree compared to older respondents###

```{r}
all_bid_readguide %>% 
  group_by(group, age_numeric) %>% 
  summarise(
        `Driving at speed limit reduces chances of crashing` = mean(perception_reduces_crash),
        `Socially acceptable to exceed limits by 5mph`= mean(perception_5mph_acceptable),
        `Unacceptable to exceed limits more than 15mph` = mean(perception_15mph_notacceptable),
        `Speeding is very dangerous` = mean(danger)
  ) %>%
  melt(id.var=c('group','age_numeric')) %>%
  ggplot(.,aes(x=age_numeric, y=value, colour=group)) +
  geom_point() + 
  geom_smooth(method='lm', linetype='dotted', size=.8, se=F) +
  geom_line() +
  scale_x_continuous(breaks=pretty_breaks(15)) +
  facet_wrap(~variable) + 
  ggtitle('Age') + 
  theme(plot.title = element_text(hjust = 0.5),
        legend.title=element_blank()) + 
  scale_color_manual(values=c('#000000',"#23b7fbff"))
```
```{r}

```


```{r, include=FALSE}
#Look at hypothetical intervention situation
intervened <- all_bid_readguide%>%
  group_by(group)%>%
  filter(!is.na(intervention))%>%
  count(intervention, sort=TRUE)%>%
  mutate(pct=round(n/sum(n),4),
         intervention=
           factor(intervention,c("Do nothing", "Comment on it but not force them to slow down", "Ask them directly to slow down")))
```

```{r,include=FALSE}
#Bar charts
intervened_chart <- ggplot(intervened, aes(x=intervention, y=pct, group = group, fill=group)) + 
                        geom_bar(stat="identity", position = "dodge", colour="grey") +
                        geom_text(aes(label=scales::percent(pct)), 
                                  vjust=-1, position = position_dodge(width=0.9),  size=3) + 
                        labs(x= 'Severity of intervention', y = 'Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                                           limits = c(0, 0.7)) + 
                        theme(axis.text.x = element_text(angle = 15, hjust = 1), 
                              legend.position="top", legend.title=element_blank(),
                              plot.title = element_text(hjust = 0.5),
                              axis.title.x = element_blank(),
                              axis.title.y = element_blank()) + 
                        ggtitle("If you are a passenger in a vehicle and the driver is driving at least 15 \n miles per hour over the speed limit, which of the following \n would you be most likely to do?") +
                        scale_fill_manual(values=c('#000000',"#23b7fbff"))

```

###INTERVENTION###

###_If you are a passenger in a vehicle and the driver is driving at least 15 \n miles per hour over the speed limit, which of the following \n would you be most likely to do?_###

####We saw a significant improvement on likelihood to intervene using the most severe intervention (p<0.05)####

    64% of participants sid they would ask a speeding driver directly to slow down vs. 44% of the control
    
```{r}
intervened_chart
```

```{r, include=FALSE}
#Chi-square test to test significance of difference
CrossTable(all_bid_readguide$intervention, all_bid_readguide$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))
```

###_In the last two weeks have you witnessed someone speeding in a vehicle?_###
####The majority (73%) witnessed someone speeding in the last two weeks####


```{r}
#Witnessed speeding
count(all_bid_readguide, witnessed_speeding, sort = TRUE)%>%
  mutate(pct=round(n/sum(n)*100,2))
```

###_Did you attempt in any way to convince the driver to slow down?_###
####We saw a significant improvement on actual intervention on a driver who is speeding (p>0.05)####

    49% of those who participated in BID said they intervened vs. 38% of the control group

```{r, include=FALSE}
#Look at actual intervention behavior
intervened_actual <- all_bid_readguide%>%
  group_by(group)%>%
  filter(!is.na(attempted_intervention_dummy))%>%
  count(attempted_intervention_dummy, sort=TRUE)%>%
  mutate(pct=round(n/sum(n),4))
```

```{r, include=FALSE}
#Bar charts
intervened_actual_chart <- ggplot(intervened_actual, aes(x=attempted_intervention_dummy, y=pct, group = group, fill=group)) + 
                        geom_bar(stat="identity", position = "dodge", colour="grey") +
                        geom_text(aes(label=scales::percent(pct)), 
                                  vjust=-1, position = position_dodge(width=0.9),  size=3) + 
                        labs(x= 'Tried to convince them to slow down', y = 'Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                                           limits = c(0, 0.7)) + 
                        theme(axis.text.x = element_text(angle = 0, hjust = 1), 
                              legend.position="top", legend.title=element_blank(),
                              plot.title = element_text(hjust = 0.5),
                              axis.title.x = element_blank(),
                              axis.title.y = element_blank()) + 
                        ggtitle("Did you attempt in any way to convince the driver to slow down?") +
                        scale_fill_manual(values=c('#000000',"#23b7fbff"))
```

```{r}
intervened_actual_chart
```



```{r, include=FALSE}
#Chi-square test to test significance of difference
CrossTable(all_bid_readguide$attempted_intervention_dummy, all_bid_readguide$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))
```

####The majority (69%) of those who intervened asked the driver in a straight forward manner to convince them to slow down####

```{r, include=FALSE}
#Only look at those who intervened 
intervention_methods <- all_bid_readguide%>%
  filter(attempted_intervention_dummy=="Yes")%>%
  select(starts_with('intervened'), -intervened_other)

#Calculate sums of each intervention dummy variable
methods_ct <- colSums(intervention_methods)
#reshape from short to long
methods_ct <-melt(methods_ct)%>%
             select(value)

#Grab column names and reshape to long
interventions <-colnames(intervention_methods)
interventions <- melt(interventions)%>%
                 rename(intervention=value)

#combine columns and totals
interventions_merged <-cbind(methods_ct,interventions)
#add percent
interventions_pct <- interventions_merged%>%
  mutate(pct=round(value/nrow(intervention_methods),4),
         intervention=
           case_when(
             intervention == 'intervened_asked' ~ 'Asked directly',
             intervention == 'intervened_stats' ~ 'Shared speed safety statistics',
             intervention == 'intervened_jokes' ~ 'Lighthearted tactics (e.g. jokes)',
             intervention == 'intervened_honked' ~ 'Honked horn',
             intervention == 'intervened_shouted' ~ 'Shouted at them')
           )

#quickly check counts match chart
# count(intervention_methods, intervened_asked, sort = TRUE)%>%mutate(pct=round(n/sum(n)*100,2))
# count(intervention_methods, intervened_stats, sort = TRUE)%>%mutate(pct=round(n/sum(n)*100,2))
# count(intervention_methods, intervened_jokes, sort = TRUE)%>%mutate(pct=round(n/sum(n)*100,2))
# count(intervention_methods, intervened_honked, sort = TRUE)%>%mutate(pct=round(n/sum(n)*100,2))
# count(intervention_methods, intervened_shouted, sort = TRUE)%>%mutate(pct=round(n/sum(n)*100,2))

```

```{r, inclue=FALSE}
#Bar chart
methods_chart <- ggplot(interventions_pct, aes(x=intervention, y=pct)) + 
                        geom_bar(stat="identity", width= 0.75, position = "dodge", fill="#FF6666") +
                        geom_text(aes(label=scales::percent(pct)), 
                                  vjust=-1, position =position_dodge(width=0.9),  size=3) + 
                        labs(x = 'Method used', y = 'Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                                           limits = c(0, .80)) + 
                        theme(axis.text.x = element_text(angle = 15, hjust = 1), 
                              legend.position="top", legend.title=element_blank(),
                              axis.title.x = element_blank(),
                              axis.title.y = element_blank()) + 
                        ggtitle("What methods did you use to convince the driver to slow down?") +
                        scale_fill_manual(values=c('#000000',"#23b7fbff"))
```

```{r}
methods_chart
```



