---
title: "Escape the Vape Survey Analyses"
output: html_notebook
---

```{r, include = FALSE}
library(gmodels)
library(glue)
library(tidyverse)
library(reshape2)
library(scales)
library(ggpubr)
library(dplyr)
```


```{r, include = FALSE}
#############################################################
################ QUIZ DATA #######################
#############################################################

#Pull Quiz data
etv_quiz <- ("SELECT 
               e.records #>> '{_id,$oid}' AS event_id,
               to_timestamp((e.records #>> '{meta,timestamp}')::bigint/1000) AS meta_timestamp,
               e.records #>> '{user,northstarId}' AS northstar_id,
               e.records #>> '{page,path}' AS url,
               e.records #>> '{event,name}' AS converted_on_quiz,
               e.records #> '{data,responses}' ->> '0' AS response_1,
               e.records #> '{data,responses}' ->> '1' AS response_2,
               e.records #> '{data,responses}' ->> '2' AS response_3,
               e.records #> '{data,responses}' ->> '3' AS response_4,
               e.records #> '{data,responses}' ->> '4' AS response_5
             FROM puck.events_json e
             WHERE e.records #>> '{data,responses}' IS NOT NULL 
             AND e.records #>> '{page,path}' ILIKE '%vape-quiz%'
             AND e.records #>> '{event,name}' = 'converted on quiz'
             AND e.records #>> '{user,northstarId}' IS NOT NULL")

etv_quiz<- runQuery(etv_quiz)

#remove duplicates
etv_quiz <- etv_quiz%>%
  filter(!duplicated(northstar_id))

#Create vars
etv_quiz <- etv_quiz%>%
            mutate_at(vars(starts_with('response')), function(x) as.numeric(substr(x, 1, 1)))%>%
            mutate(
              aerosol = 
                 case_when(response_1==0 ~ 'True',
                           response_1==1 ~ 'False'),
               nicotine = 
                 case_when(response_2==0~'True',
                           response_2==1 ~ 'False'),
               jul_pod = 
                 case_when(response_3==0 ~ 'True',
                           response_3==1 ~ 'False'),
               jul_designed = 
                 case_when(response_4==0~'True',
                           response_4==1 ~ 'False'),
               ecig_flavors = 
                 case_when(response_5==0~'True',
                           response_5==1 ~ 'False'),
              total_wrong = rowSums(.[grep("response", names(.))], na.rm = TRUE),
              all_correct = if_else(total_wrong==0,"All correct", "At least one wrong")
                   ) 
```

#ESCAPE THE VAPE ONLINE QUIZ#

###_The aerosol from e-cigs usually contains nicotine and can contain toxic and cancer-causing chemicals, like formaldehyde and heavy metals._ ###
```{r}
count(etv_quiz, aerosol, sort = TRUE)%>%
  mutate(pct=percent(n/sum(n)))
```

###_Highly addictive nicotine can harm development of a young person’s brain._###

```{r}
count(etv_quiz, nicotine, sort = TRUE)%>%
  mutate(pct=percent(n/sum(n)))
```

###_One JUUL pod contains the same amount of nicotine as an entire pack of cigarettes._###

```{r}
count(etv_quiz, jul_pod, sort = TRUE)%>%
  mutate(pct=percent(n/sum(n)))
```

###_Some e-cigs like JUUL were designed intentionally to not look like regular cigarettes, and instead resemble everyday items like USB drives, pens and markers._###

```{r}
count(etv_quiz, jul_designed, sort = TRUE)%>%
  mutate(pct=percent(n/sum(n)))
```

###_Youth e-cig users say flavors are one of the main reasons they use these products._###

```{r}

count(etv_quiz, ecig_flavors, sort = TRUE)%>%
  mutate(pct=percent(n/sum(n)))
```


### 79% of quiz takers got all the questions correct###

```{r}
#Pct got all correct
count(etv_quiz, all_correct, sort = TRUE)%>%
  mutate(pct=percent(n/sum(n)))

count(etv_quiz, total_wrong, sort = TRUE)%>%
  mutate(pct=percent(n/sum(n)))
```

#ESCAPE THE VAPE SURVEY#
```{r}
## Upload experiment/control surveys and rename columns

#Upload Typeform Escape the Vape responses 
etv_experiment <- read.csv('~/Documents/Escape the Vape/Escape the Vape Feb 1.csv',na.strings=c("", "NA"))
etv_experiment$group = "participants"

#Upload Control survey data
etv_control <-read.csv('~/Documents/Escape the Vape/What are your thoughts on e-cigarettes Feb 1.csv', na.strings=c("", "NA"))
etv_control$group = "control"

#Combine Control and Experiment surveys 
etv_all <- bind_rows(etv_experiment,etv_control)

#Rename columns

etv_all <- etv_all%>%
  rename(gender=What.is.your.gender.,
         gender_other=Other,
         age=How.old.are.you.,
         region=What.type.of.region.do.you.live.in.,
         freq_vape=How.often.would.you.say.you.are.exposed.to.vaping.e.cigarette.smoke.,
         reason_cheaper=It.s.cheaper.than.smoking.cigarettes,
         reason_lessdanger=They.think.it.s.less.dangerous.than.cigarettes,
         reason_taste=They.like.the.taste.of.the.flavors,
         reason_cool=They.think.it.s.cool,
         reason_friends=Their.friends.are.doing.it,
         reason_parents=Their.parents.smoke,
         reason_stress=To.help.with.stress,
         reason_harmless=They.think.it.s.harmless,
         reason_other=Other.1,
         agree_marketing=E.cigarette.companies.use.marketing.tactics.to.target.young.people,
         agree_hidedangers=E.cigarette.companies.intentionally.hide.the.dangers.of.vaping.so.more.people.will.buy.their.products,
         agree_tobacco=Tobacco.use.in.any.form..including.e.cigarettes.like.JUUL..vape.pens..mods..e.hookas..and.tank.systems..is..strong.not..strong..safe,
         read_guide=Did.you.read.our...em.7.THINGS.E.CIG.AND.VAPE.COMPANIES.DON.T.WANT.YOU.TO.KNOW...em..guide.,
         guide_thoughts=What.did.you.think.about.the.content.in.the.guide.,
         smoker_stop=If.you.are.a.current.smoker..do.you.want.to.stop.vaping..now.or.in.the.future..,
         intervention=If.you.were.to.witness.a.friend.or.family.member.vaping..which.of.the.following.would.you.be.most.likely.to.do.,
         thought_differently=Have.you.thought.differently.about.vaping.since.participating.in.Escape.the.Vape.,
         thought_differently_how=How.have.you.thought.differently.,
         nps=Based.on.your.experience..how.likely.would.you.be.to.recommend.DoSomething.to.a.friend.,
         suggestions=If.you.have.any.suggestions.on.how.we.could.improve.this.campaign.or.your.experience..please.share.below.)

#remove duplicate emails and irrelevant vars
etv_all <- etv_all%>%
  filter(!duplicated(id))%>%
  select(-X.,Network.ID)
```

```{r}
#Create new vars
etv_all <-etv_all%>%
  mutate_at(vars(starts_with('reason')), .funs = funs(ifelse(is.na(.), 0, 1)))%>%
  mutate(survey_submit = as.Date(paste0(Submit.Date..UTC., ':00'), '%m/%d/%y %H:%M:%S'),
          gender =
             case_when(
               gender == 'Woman' ~ 'Female',
               gender == 'Man' ~ 'Male',
               TRUE ~ 'Other'),
           age =
            case_when(
               age == 'Older than 25' ~ '26',
               age == 'Younger than 15' ~ '14',
               TRUE ~ as.character(age)),
           age_numeric = as.numeric(age)
    )
```


```{r}
# demographics for each group
CrossTable(etv_all$gender, etv_all$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))

CrossTable(etv_all$region, etv_all$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))

CrossTable(etv_all$age, etv_all$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))

CrossTable(etv_all$freq_vape, etv_all$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))
```

### Almost half (49%) said they were exposed to vaping/e-cigarette smoke at least once a week ###

```{r}
#look at freq exposed to vaping by group
freq_vape_group <- etv_all%>%
  group_by(group)%>%
  count(freq_vape, sort=TRUE)%>%
  mutate(pct=(n/sum(n)),
         freq_vape=
           factor(
             case_when(
               freq_vape=='A few times a month' ~ 'Few times a month',
               freq_vape=='A few times a week' ~ 'Few times a week',
               freq_vape=='Everyday' ~ 'Everyday',
               freq_vape=='Less than a few times a month' ~ '< Few times a month',
               freq_vape=='Never' ~ 'Never',
               freq_vape=='Not sure' ~ 'Not sure'), 
                levels=c('Never','Not sure','< Few times a month', 'Few times a month','Few times a week','Everyday'))
          )

#look at freq exposed to vaping overall
freq_vape <- count(etv_all,freq_vape, sort=TRUE)%>%
  mutate(pct=(n/sum(n)),
         freq_vape=
           factor(
             case_when(
               freq_vape=='A few times a month' ~ 'Few times a month',
               freq_vape=='A few times a week' ~ 'Few times a week',
               freq_vape=='Everyday' ~ 'Everyday',
               freq_vape=='Less than a few times a month' ~ '< Few times a month',
               freq_vape=='Never' ~ 'Never',
               freq_vape=='Not sure' ~ 'Not sure'), 
                levels=c('Never','Not sure','< Few times a month', 'Few times a month','Few times a week','Everyday'))
          )

#bar chart by group
freq_vape_chart_group<- ggplot(freq_vape_group, aes(x=freq_vape, y=pct, group = group, fill=group)) + 
                        geom_bar(stat="identity", width= 0.75, position = "dodge") +
                        geom_text(aes(label=scales::percent(pct)), 
                                  vjust=-1, position =position_dodge(width=0.9),  size=3) + 
                        ylab('Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                                           limits = c(0, 0.5)) + 
                        theme(plot.title = element_text(hjust = 0.5),
                              axis.text.x = element_text(angle = 15, hjust = 1), 
                              legend.position="top", legend.title=element_blank(),
                              axis.title.x=element_blank(),
                              axis.title.y=element_blank()) + 
                        ggtitle("How often would you say you are exposed to vaping/e-cigarette smoke?") +
                        scale_fill_manual(values=c('#fcd116ff',"#23b7fbff"))

#bar chart
freq_vape_chart<- ggplot(freq_vape, aes(x=freq_vape, y=pct)) + 
                        geom_bar(stat="identity", width= 0.75, position = "dodge", fill="#4e2b63ff") +
                        geom_text(aes(label=scales::percent(pct)), 
                                  vjust=-1, position =position_dodge(width=0.9),  size=3) + 
                        ylab('Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                                           limits = c(0, 0.5)) + 
                        theme(plot.title = element_text(hjust = 0.5),
                              axis.text.x = element_text(angle = 15, hjust = 1), 
                              legend.position="top", legend.title=element_blank(),
                              axis.title.x=element_blank(),
                              axis.title.y=element_blank()) + 
                        ggtitle("How often would you say you are exposed to vaping/e-cigarette smoke?") 
```

```{r}
print(freq_vape_chart_group)
print(freq_vape_chart)
```

```{r}
ggsave("vape_exposure.png", width = 8, height=5,dpi=300)
```


### Participants were more likely to agree that E-cigarette use marketing tactics to target young people ###

```{r, include = FALSE}
agree_marketing <- etv_all%>%
  group_by(group)%>%
  filter(!is.na(agree_marketing))%>%
  count(agree_marketing, sort=TRUE)%>%
  mutate(pct=round(n/sum(n),4),
         agree_marketing=
           factor(
             case_when(
               agree_marketing == 1 ~ 'Strongly Disagree',
               agree_marketing == 2 ~ '2',
               agree_marketing == 3 ~ '3',
               agree_marketing == 4 ~ '4',
               agree_marketing == 5 ~ 'Strongly Agree'),
                levels = c("Strongly Disagree", "2", "3", "4", "Strongly Agree")))

freq_residential <- all_bid_readguide%>%
  group_by(group)%>%
  filter(!is.na(speeding_freq_residential_numeric) & !is.na(speeding_freq_residential))%>%
  count(speeding_freq_residential, sort=TRUE)%>%
  mutate(pct=round(n/sum(n),4),
         speeding_freq_residential=
           factor(speeding_freq_residential,c("Never", "Rarely", "Sometimes", "Often")))
```

```{r, include = FALSE}
#Bar charts
agree_marketing_chart <- ggplot(agree_marketing, aes(x=agree_marketing, y=pct, group = group, fill=group)) + 
                        geom_bar(stat="identity", position = "dodge", colour="grey") +
                        geom_text(aes(label=scales::percent(pct)), vjust=-1, position = position_dodge(width=0.9),  size=3) + 
                        labs(x = 'Frequency', y = 'Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 0.7)) + 
                        theme(axis.text.x = element_text(angle = 20, hjust = 1), legend.position="top", 
                              legend.title=element_blank(),
                              axis.title.x=element_blank(),
                              axis.title.y=element_blank(),
                              plot.title = element_text(hjust = 0.5, face="bold")) + 
                        ggtitle("E-cigarette companies use marketing tactics to target young people") +
                        scale_fill_manual(values=c('#fcd116ff',"#23b7fbff"))
```

```{r}
print(agree_marketing_chart)
```

```{r}
ggsave("target.png", width=9, height=5, dpi=300)
```


```{r, include= FALSE}
#test significance of differences
CrossTable(etv_all$agree_marketing, etv_all$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))
```

### Participants were more likely to agree that E-cigarette companies intentionally hide the dangers of vaping ###

```{r, include = FALSE}
agree_hidedangers <- etv_all%>%
  group_by(group)%>%
  filter(!is.na(agree_hidedangers))%>%
  count(agree_hidedangers, sort=TRUE)%>%
  mutate(pct=round(n/sum(n),4),
         agree_hidedangers=
           factor(
             case_when(
               agree_hidedangers == 1 ~ 'Strongly Disagree',
               agree_hidedangers == 2 ~ '2',
               agree_hidedangers == 3 ~ '3',
               agree_hidedangers == 4 ~ '4',
               agree_hidedangers == 5 ~ 'Strongly Agree'),
                levels = c("Strongly Disagree", "2", "3", "4", "Strongly Agree")))
```

```{r, include = FALSE}
#Bar charts
agree_hidedangers_chart <- ggplot(agree_hidedangers, aes(x=agree_hidedangers, y=pct, group = group, fill=group)) + 
                        geom_bar(stat="identity", position = "dodge", colour="grey") +
                        geom_text(aes(label=scales::percent(pct)), vjust=-1, position = position_dodge(width=0.9),  size=3) + 
                        labs(x = 'Frequency', y = 'Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 0.7)) + 
                        theme(axis.text.x = element_text(angle = 20, hjust = 1), legend.position="top", 
                              legend.title=element_blank(),
                              axis.title.x=element_blank(),
                              axis.title.y=element_blank(),
                              plot.title = element_text(hjust = 0.5, face = "bold")) + 
                        ggtitle("E-cigarette companies intentionally hide the dangers of vaping so more \n people will buy their products") +
                        scale_fill_manual(values=c('#fcd116ff',"#23b7fbff"))
```

```{r}
print(agree_hidedangers_chart)
```

```{r}
ggsave("hide_dangers.png", width=9, height=5, dpi=300)
```

```{r, include= FALSE}
#test significance of differences
CrossTable(etv_all$agree_hidedangers, etv_all$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))
```

```{r, include = FALSE}
agree_tobacco <- etv_all%>%
  group_by(group)%>%
  filter(!is.na(agree_tobacco))%>%
  count(agree_tobacco, sort=TRUE)%>%
  mutate(pct=round(n/sum(n),4),
         agree_marketing=
           factor(
             case_when(
               agree_tobacco == 1 ~ 'Strongly Disagree',
               agree_tobacco == 2 ~ '2',
               agree_tobacco == 3 ~ '3',
               agree_tobacco == 4 ~ '4',
               agree_tobacco == 5 ~ 'Strongly Agree'),
                levels = c("Strongly Disagree", "2", "3", "4", "Strongly Agree")))
```

```{r, include = FALSE}
#Bar charts
agree_tobacco_chart <- ggplot(agree_tobacco, aes(x=agree_tobacco, y=pct, group = group, fill=group)) + 
                        geom_bar(stat="identity", position = "dodge", colour="grey") +
                        geom_text(aes(label=scales::percent(pct)), vjust=-1, position = position_dodge(width=0.9),  size=3) + 
                        labs(x = 'Frequency', y = 'Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 0.9)) + 
                        theme(axis.text.x = element_text(angle = 20, hjust = 1), legend.position="top", 
                              legend.title=element_blank(),
                              axis.title.x=element_blank(),
                              axis.title.y=element_blank(),
                              plot.title = element_text(hjust = 0.5, face="bold")) + 
                        ggtitle("Tobacco use in any form (including e-cigarettes like JUUL, vape pens, mods, \n e-hookas, and tank systems) is not safe") +
                        scale_fill_manual(values=c('#fcd116ff',"#23b7fbff"))
```

### There was no difference in belief that tobacco is not safe between the groups ###

```{r}
print(agree_tobacco_chart)
```
```{r}
ggsave("tobacco.png", width=9, height=5, dpi=300)
```


```{r, include= FALSE}
CrossTable(etv_all$agree_tobacco, etv_all$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))
```


```{r, include=FALSE}
etv_reasons <- etv_all%>%
  select(contains('reason'))

#only look at feelings
reasons <- etv_reasons%>%
  select(starts_with('reason'))
#Calculate sum of 1s for each feeling dummy variable
reasons_ct <- colSums(reasons)
#reshape from short to long
reasons_ct <-melt(reasons_ct)%>%
             select(value)

#Grab column names and reshape to long
reasons_names <-colnames(reasons)
reasons_names <- melt(reasons_names)%>%
                 rename(reasons=value)

#combine column names and totals and add pct
reasons_merged <-cbind(reasons_ct,reasons_names)%>%
  mutate(pct=round(value/nrow(etv_reasons),4),
         reasons=
           factor(
             case_when(
               grepl('cool', reasons) ~ 'Think its cool',
               grepl('danger', reasons) ~ 'Less dangerous than cigarettes',
               grepl('taste', reasons) ~ 'Like the taste of flavors',
               grepl('friends', reasons) ~ 'Friends are doing it',
               grepl('harmless', reasons) ~ 'Think its harmless',
               grepl('stress', reasons) ~ 'Help with stress',
               grepl('cheaper', reasons) ~ 'Cheaper than cigarettes',
               grepl('parent', reasons) ~ 'Parents smoke'),
                levels=c('Think its cool','Less dangerous than cigarettes','Friends are doing it',
                         'Like the taste of flavors','Think its harmless','Help with stress','Cheaper than cigarettes',
                         'Parents smoke'))
           )%>%
  filter(!is.na(reasons))

```

```{r, include=FALSE}
#Bar chart
reasons_chart <- ggplot(reasons_merged, aes(x=reasons, y=pct)) + 
                        geom_bar(stat="identity", width= 0.75, position = "dodge", fill="#23b7fbff") +
                        geom_text(aes(label=scales::percent(pct)), 
                                  vjust=-1, position =position_dodge(width=0.9),  size=3) + 
                        ylab('Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                                           limits = c(0, .80)) + 
                        theme(axis.text.x = element_text(angle = 25, hjust = 1), 
                              legend.position="top", legend.title=element_blank(),
                              axis.title.x=element_blank(),
                              axis.title.y=element_blank(),
                              plot.title = element_text(hjust = 0.5, face="bold")) + 
                        ggtitle("What do you think are the main reasons people your age vape (use e-cigarettes)?")
```

### Most thought young people use e-cigarettes because they think it's cool, think it's less dangerous than cigarettes, they're friends are doing it, they like the taste of flavors, and they think it's harmless ###

```{r}
reasons_chart
```

ggsave("")
```{r}
ggsave("reasons.png", width=8, height=5, dpi=300)
```

### Few were current smokers ###

```{r, include = FALSE}
smoker <- etv_all%>%
  group_by(group)%>%
  filter(!is.na(smoker_stop))%>%
  count(smoker_stop, sort=TRUE)%>%
  mutate(pct=round(n/sum(n),4),
         smoker_stop=
           factor(
             case_when(
               grepl('Don', smoker_stop) ~ 'Dont know',
               grepl('not', smoker_stop) ~ 'Not a smoker',
               grepl('No', smoker_stop) ~ 'No',
               grepl('Yes', smoker_stop) ~ 'Yes'),
                levels = c("Not a smoker", "Dont know", "No", "Yes"))
         )
```

```{r, include = FALSE}
#Bar charts
smoker_chart <- ggplot(smoker, aes(x=smoker_stop, y=pct, group = group, fill=group)) + 
                        geom_bar(stat="identity", position = "dodge", colour="grey") +
                        geom_text(aes(label=scales::percent(pct)), vjust=-1, position = position_dodge(width=0.9),  size=3) + 
                        labs(x = 'Frequency', y = 'Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) + 
                        theme(axis.text.x = element_text(angle = 20, hjust = 1), legend.position="top", 
                              legend.title=element_blank(),
                              axis.title.x=element_blank(),
                              axis.title.y=element_blank(),
                              plot.title = element_text(hjust = 0.5)) + 
                        ggtitle("If you are a current smoker, do you want to stop vaping (now or in the future?)") +
                        scale_fill_manual(values=c('#fcd116ff',"#23b7fbff"))
```

```{r}
print(smoker_chart)
```

```{r}
ggsave("smoker.png", width=9, height=5, dpi=300)
```

```{r, include= FALSE}
CrossTable(etv_all$smoker_stop, etv_all$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))
```

```{r, include = FALSE}
intervention <- etv_all%>%
  group_by(group)%>%
  filter(!is.na(intervention))%>%
  count(intervention, sort=TRUE)%>%
  mutate(pct=round(n/sum(n),4),
         intervention=
           factor(
             case_when(
               grepl('Comment', intervention) ~ 'Comment',
               grepl('Do nothing', intervention) ~ 'Do nothing',
               grepl('Don', intervention) ~ 'Dont know',
               grepl('Try', intervention) ~ 'Convince them to stop'),
                levels = c("Do nothing", "Dont know", "Comment", "Convince them to stop"))
         )
```

```{r, include = FALSE}
#Bar charts
intervention_chart <- ggplot(intervention, aes(x=intervention, y=pct, group = group, fill=group)) + 
                        geom_bar(stat="identity", position = "dodge", colour="grey") +
                        geom_text(aes(label=scales::percent(pct)), vjust=-1, position = position_dodge(width=0.9),  size=3) + 
                        labs(x = 'Frequency', y = 'Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 0.7)) + 
                        theme(axis.text.x = element_text(angle = 20, hjust = 1), legend.position="top", 
                              legend.title=element_blank(),
                              axis.title.x=element_blank(),
                              axis.title.y=element_blank(),
                              plot.title = element_text(hjust = 0.5, face="bold")) + 
                        ggtitle("If you were to witness a friend or family member vaping, \n which of the following would you be most likely to do?") +
                        scale_fill_manual(values=c('#fcd116ff',"#23b7fbff"))
```

```{r}
print(intervention_chart)
```

```{r}
ggsave("witness.png", width=9,height=5,dpi=300)
```

```{r, include= FALSE}
CrossTable(etv_all$intervention, etv_all$group, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))
```
### 48% said they read the guide ###

```{r}
guide <- etv_all%>%
   filter(group=='participants' & !is.na(read_guide))%>%
      count(read_guide, sort = TRUE)%>%
      mutate(pct=percent(n/sum(n)))%>%
      print()
```

```{r}
#Look at only participants
guide <- etv_all%>%
   filter(group=='participants' & !is.na(read_guide))

guide <- guide%>%
  mutate(
    read_guide=
           case_when(
             read_guide==0 ~ 'Did not read guide',
             read_guide==1 ~ 'Read guide'))%>%
  group_by(read_guide)%>%
  filter(!is.na(intervention))%>%
  count(intervention, sort=TRUE)%>%
  mutate(pct=round(n/sum(n),4),
         intervention=
           factor(
             case_when(
               grepl('Comment', intervention) ~ 'Comment',
               grepl('Do nothing', intervention) ~ 'Do nothing',
               grepl('Don', intervention) ~ 'Dont know',
               grepl('Try', intervention) ~ 'Convince them to stop'),
                levels = c("Do nothing", "Dont know", "Comment", "Convince them to stop"))
         )
```

```{r, include = FALSE}
#Bar charts
guide_chart <- ggplot(guide, aes(x=intervention, y=pct, group = read_guide, fill=read_guide)) + 
                        geom_bar(stat="identity", position = "dodge", colour="grey") +
                        geom_text(aes(label=scales::percent(pct)), vjust=-1, position = position_dodge(width=0.9),  size=3) +
                        labs(x = 'Frequency', y = 'Percentage') + 
                        scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 0.7)) + 
                        theme(axis.text.x = element_text(angle = 20, hjust = 1), legend.position="top", 
                              legend.title=element_blank(),
                              axis.title.x=element_blank(),
                              axis.title.y=element_blank(),
                              plot.title = element_text(hjust = 0.5, face="bold")) + 
                        ggtitle("If you were to witness a friend or family member vaping, \n which of the following would you be most likely to do??)") +
                        scale_fill_manual(values=c('#fcd116ff',"#23b7fbff"))
```

### Those who read the guide more likely to intervene ###

```{r}
print(guide_chart)
```
```{r}
ggsave("guide.png", width=9, height=5, dpi=300)
```


```{r, include=FALSE}
#check significance
guide <- etv_all%>%
   filter(group=='participants' & !is.na(read_guide))

CrossTable(guide$intervention, guide$read_guide, prop.c=TRUE, prop.r=FALSE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, missing.include = FALSE,format= c("SPSS"))
```



