---
title: "Multiple Campaigns and Rbs Data Request"
output: html_notebook
---

```{r}
#Request: #https://trello.com/c/PFl9hk7X/1412-members-who-sign-up-for-multiple-campaigns-and-reportbacks
library(dplyr)
library(tidyverse)
#set environment time zone so R pulls timestamps in correctly from Quasar 
Sys.setenv(TZ='UTC') 
```

```{r}
#Pull members who signed up in the last year, their max/min dates, and total their signups/rbs for only photo posts
active_last6month <- ("SELECT signups.*,rbs.total_rbs, rbs.last_rb, rbs.first_rb
                          FROM
                            ((SELECT 
                                s.northstar_id  AS nsid,
	                              COUNT(DISTINCT(s.id)) AS total_signups,
                                max(s.created_at) as last_signup,
                                min(s.created_at) as first_signup
                            FROM public.signups s
                            INNER JOIN public.users u ON u.northstar_id=s.northstar_id
                              WHERE u.email IS NOT NULL 
                              AND s.created_at > now() - INTERVAL ' 1 year'
                              AND s.campaign_run_id NOT IN ('8176', '8227', '8291')
                              AND s.campaign_id NOT IN ('8176', '8226', '8303', '8291')
                            GROUP BY s.northstar_id) signups
                          LEFT JOIN 
                              (SELECT 
                                posts.northstar_id  AS nsid,
                                COUNT(DISTINCT(posts.id)) AS total_rbs,
                                max(posts.created_at) as last_rb,
                                min(posts.created_at) as first_rb
                              FROM public.posts posts
                              WHERE posts.TYPE IN ('photo')
                              GROUP BY posts.northstar_id) rbs
                              ON signups.nsid=rbs.nsid)" 
)

active_last6month <- runQuery(active_last6month)

```

```{r}
#create variables for time between first and last signup/rb
email_activity <- active_last6month%>%
  mutate(multiple_signup=ifelse(total_signups>1,'2+ signups','1 or less signup'),
         multiple_rb=ifelse(total_rbs>1,'2+ rbs','1 or less rb'),
         hours_between_signup = difftime(last_signup, first_signup, units = "hours"),
         hours_between_rb = difftime(last_rb, first_rb, units = "hours"),
         days_between_signup = difftime(last_signup, first_signup, units = "days"),
         days_between_rb = difftime(last_rb, first_rb, units = "days"),
         time_multiple_signups = 
              case_when(days_between_signup<1 & total_signups>=2 ~ 'On same day',
                        days_between_signup>=1 & days_between_signup <3 & total_signups>=2 ~ 'Within 1-2 days',
                        days_between_signup>=3 & days_between_signup <8 & total_signups>=2 ~ 'Within 3- 7 days',
                        days_between_signup>7 & total_signups>=2 ~ 'Within 8+ days'),
         time_multiple_rbs = 
           case_when(days_between_rb<1 & total_rbs>=2 ~ 'On same day',
                     days_between_rb>=1 & days_between_rb <3 & total_rbs>=2 ~ 'Within 1-2 day',
                     days_between_rb>=3 & days_between_rb <8 & total_rbs>=2 ~ 'Within 3- 7 days',
                     days_between_rb>7 & total_rbs>=2 ~ 'Within 8+ days')
           )
```

**SIGNUPS**

* *The majority of those who signed up in the last year only signed up for 1 campaign*
```{r}
#Plot count of signups/member
ggplot(email_activity, aes(x=total_signups)) +
  geom_bar() + geom_text(stat='count',aes(label=..count..),vjust=-1) + xlim(c(0,15)) + 
  ylim(c(0,600000)) +
  labs(x='Number of signups/member in the last year', title = 'Signups per member in the last year')
```

* *Only 27% of members who signed up in the last year signed up for 2+ campaigns*
```{r}
#Pct of members with 2+ signups in the last year
count(email_activity, multiple_signup, sort = TRUE)%>%mutate(pct=n/sum(n)*100)
```

* *Overall, only 5% of members signed up for mutliple campaigns on the same day.*
```{r}
#Distribution of when members signed up
count(email_activity, time_multiple_signups, sort = TRUE)%>%mutate(pct=n/sum(n)*100)
```

* *Looking at **only** those with 2+ signups, the majority (71%) signed up for multiple campaigns over a week after their first campaign. *
* *20% signed up for more than one campaign on the same day.*

```{r}
#Look at only multiple signups
multiple_signups <- email_activity%>%
  filter(multiple_signup=='2+ signups')%>%
  mutate(days_between_signup=as.numeric(days_between_signup))

#Number of days between multiple signups
count(multiple_signups, time_multiple_signups)%>%mutate(pct=n/sum(n)*100)

#Plot above
ggplot(multiple_signups, aes(x=time_multiple_signups)) + geom_bar() +
  geom_text(stat='count',aes(label=..count..),vjust=-1) +
  ylim(c(0,150000)) +
  labs(x='Duration between first and last signup', title = 'Members with multiple signups in the last year') 
```
* *For multiple signups on the same day, the median time between the first and last signup time for multiple signups was 0.14hrs.*
```{r}
#Look at only multiple signups on same day
multiple_signup_sameday <- multiple_signups%>%
  filter(time_multiple_signups=='On same day')%>%
  mutate(hours_between_signup=as.numeric(hours_between_signup))

#look at median/mean number of hours between first and last sign up
summary(multiple_signup_sameday$hours_between_signup)

```

```{r}
#Looks at density of 2 hours
ggplot(multiple_signup_sameday, aes(x=hours_between_signup)) +
  geom_density() + xlim(c(0,2)) +
  labs(x='Number of hours between first and last signup', title = 'Members with 2+ signups on same day') 
```


* *The majority (81%) of members who had multiple signups in a day, only signed up for **2** campaigns.*
```{r}
#Distribution of members with 2+ signups on the same day
count(multiple_signup_sameday, total_signups, sort = TRUE)%>%mutate(pct=n/sum(n)*100)
```

**REPORTBACKS**

* *Only 3% of members who signed up for a campaign in the last year submitted 2+ photo rbs *

```{r}
#Pct of members with 2+ rbs in the last year
count(email_activity, multiple_rb, sort = TRUE)%>%mutate(pct=n/sum(n)*100)
```
* *The majority of members who submitted a photo rb only submitted 1*
```{r}
#Plot rbs/member
ggplot(email_activity, aes(x=total_rbs)) +
  geom_bar() + geom_text(stat='count',aes(label=..count..),vjust=-1) + xlim(0,10) + ylim(c(0,50000)) +
  labs(x='Count of photo rbs/member in the last year', title = 'Total photo rbs per member in the last year')
```

* *Looking at those who have multiple rbs, 32% submitted photo rbs on the same day*
```{r}
#Look at only multiple rbs
multiple_rbs <- email_activity%>%
  filter(multiple_rb=='2+ rbs')%>%
  mutate(days_between_rb=as.numeric(days_between_rb))

#Number of days between multiple rbs
count(multiple_rbs, time_multiple_rbs)%>%mutate(pct=n/sum(n)*100)

#bar chart of above
ggplot(multiple_rbs, aes(x=time_multiple_rbs)) + geom_bar() +
  geom_text(stat='count',aes(label=..count..),vjust=-1) + ylim(c(0,7000)) +
  labs(x='Duration between first and last reportback', title = 'Members with multiple reportbacks in the last year') 
```


* *For multiple photo rbs on the same day, the median time between the first and last rb was 0.2 hrs*
```{r}
#Look at only multiple rbs on same day
multiple_rb_sameday <- multiple_rbs%>%
  filter(time_multiple_rbs=='On same day')%>%
  mutate(hours_between_rb=as.numeric(hours_between_rb))

#look at median/mean number of hours between first and last rb
summary(multiple_rb_sameday$hours_between_rb)

```

```{r}
#look at number of hours for multiple rbs on a same day
ggplot(multiple_rb_sameday, aes(x=hours_between_rb)) +
  geom_density() + xlim(c(0,3)) +
  labs(x='Number of hours between first and last rb', title = 'Members with 2+ rbs on same day') 
```

* *The majority of members (70%) who had multiple photo rbs in a day, only reported back **2** times in a day.*
```{r}
#Distribution of members with 2+ signups on the same day
count(multiple_rb_sameday, total_rbs, sort = TRUE)%>%mutate(pct=n/sum(n)*100)
```
