---
title: "Super Stress Face Data Request"
output: html_notebook
---
```{r}
library(tidyverse)
library(data.table)
library(rmarkdown)
library(plyr)
library(gmodels)
```


```{r}
#Upload CSV files
groupB<-read.csv('~/Desktop/Show Stress B group.csv')
groupB$group<-"groupB"
control<-read.csv('~/Desktop/Show Stress Face Control.csv')
control$group<-"control"
```

```{r}
#Merge csv files
superstress<-rbind(groupB,control)

superstress<-showstress%>%
  mutate(
    reportedback=ifelse(total_rbs>0,'yes','no'),
    visitedsite=ifelse(site_visits>0, 'yes', 'no')
  )
```

###Control vs. Messaging - Reported back and Visited site

* **23% of those who received drip messaging reported back vs. 21% of the control group. This difference is not statistically significant (p>0.05)** 
* **98.5% of those who received drip messaging visited the site vs. 100% of the control group. This difference is statistically significant (p<0.05)**

```{r}
#Percentage reporting back and visiting site
CrossTable(superstress$group, superstress$reportedback, prop.c=FALSE, prop.r=TRUE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, format= c("SPSS"))
CrossTable(superstress$group, superstress$visitedsite, prop.c=FALSE, prop.r=TRUE, prop.t=FALSE, prop.chisq=FALSE, chisq=TRUE, format= c("SPSS"))

```

###Control vs. Messaging - Average number of RBs and Site Visits

* **The average number of report backs for those who received drip messaging was 1.14 vs. 1.04 for the control. This difference was not statistically significant** 
* **The average number of visits to site for those who received drip messaging was 3.15 vs. 3.00 for the control. This difference was not statistically significant**

```{r}
#Average number of reportbacks
group_by(superstress, group) %>%
  summarise(
    count = n(),
    mean = mean(total_rbs, na.rm = TRUE),
    sd = sd(total_rbs, na.rm = TRUE),
     var = var(total_rbs,na.rm = TRUE)
  )

```
```{r}
#Average number of site visits
group_by(superstress, group) %>%
  summarise(
    count = n(),
    mean = mean(site_visits, na.rm = TRUE),
    sd = sd(site_visits, na.rm = TRUE),
    var = var(site_visits,na.rm = TRUE)
  )
```

```{r}
#T-test for statistical significance
t.test(superstress$total_rbs~superstress$group)
t.test(superstress$site_visits~superstress$group)
```


```{r}
#Total number of reportbacks
# aggregate(showstress$total_rbs, by=list(Category=showstress$group), FUN=sum)
# 
# #Total number of site visits
# aggregate(showstress$site_visits, by=list(Category=showstress$group), FUN=sum)
# 
# render('~/Data/Trello_Requests/Super_Stress_Face.Rmd', "html_notebook")
```




