---
title: "Ride & Seek Survey Analysis"
output: html_notebook
---
```{r echo=FALSE, warnings=FALSE}
library(scales)
library(knitr)
options(scipen=5)
rerun=F
```

```{r echo=FALSE}
if (rerun==T) {
  source('Scripts/Scripts/rideSeekSurveyAnalysis.R')
} else {
  load('~/Data/AdHoc/Data/rideSeekSurveyAnalyticalSet.Rdata')
}
```

```{r echo=FALSE}
numControl <- c('age')
experiment <- c('Group')
controls <- c('gender','region','license','vehicle','driving_freq')
outcomes <- c('distraction_prone','considers_dangers','willing_intervene',
              'seatbelt_driver','seatbelt_front','seatbelt_back')
titles <- c('Gender', 'Region', 'License', 'Vehicle Type', 'Driving Frequency')
```
###Defining Outcomes
* **Seatbelt.XXX**
    + Respondents were asked how often they wear a seat belt in a vehicle, 
    with options ranging from "Never" and "Almost Never" to "Every time". 
    These responses were recoded into values between 0 and 1 with higher values for 
    more frequent seat belt usage. This was captured for when individuals were driving, 
    seated in the front, or seated in the back
        + 0 = Never/Almost Never
        + 0.25 = Less than half the time
        + .75 = At least half of time/Most of the time
        + 1 = Every time
    + We hypothesize that participating in the campaign will increase this metric
    across all three options.
* **Distractions**
    + Respondents were asked to tick off items they considered to be distractions
    while driving from a menu of options. The menu contained items such us texting,
    making phone calls, and listening to the radio. We encode each option in the menu
    as either 0 and 1 then take the mean across all the options for each survey response.
    + We hypothesize that participating in Ride & Seek will increase the number 
    the number of items the participants acknowledges as distractions while driving.
* **Interventions**
    + Respondents were asked about the types of interventions they were willing
    to engage in if they saw someone in a car without a seatbelt. The responses 
    varied in severity where the most severe was stopping the car until a seatbelt 
    was worn, and the least severe was to do nothing. These responses were coded to
    range between 0 and 1. 
        + 0 = Nothing
        + 0.25 = Don't know
        + 0.50 = Comment on it but not force them to wear it
        + 0.75 = Ask them directly to wear a seat belt
        + 1 = Stop the car until they wear a seat belt
    + We hypothesize that participants in Ride & Seek will be more willing to engage 
    in higher severity interventions.
* **Dangers**
    + Respondents were asked how dangerous they consider not wearing a seat belt 
    in the front seat, back seat, and engaging in distracting behavior on a scale
    of 1 (not very dangerous) through 5 (very dangerous). We then rescaled these values 
    to range from  0 to 1 and then  took the mean across the three questions for each respondant.
    + We hypothesize that participants in Ride & Seek will begin to acknolwedge 
    the danger of more of these activites. 
    
###Timeline of Surveys
The following shows survey submission volume over time, pivoted by experiment group. 
We see experiment surveys came in waves, as designed, whereas control group were 
distributed broadly throughout, with some bumps as we realized more control group surveys
were required.
```{r echo=FALSE}
ggplot(dat, aes(x=group,y=survey_submit,fill=group)) + 
  geom_violin(position='dodge') + 
  coord_flip() + theme(legend.position="none") + 
  labs(title='Survey Date by Group', y='Survey Submission Date', x='') + 
  theme(plot.title = element_text(hjust = 0.5))
```

###Control vs. Experiment

* **The difference on every outcome is statistically significant at alpha=0.01.** 
This suggests it is highly unlikely the effects we are seeing are spurious. 
```{r echo=FALSE}
getPval <- function(dat, outcome, metName) {
  e <- dat %>% filter(group=='experiment') %>% select(outcome)
  c <- dat %>% filter(group=='control') %>% select(outcome)
  pval <- round(t.test(unlist(e),unlist(c))$p.value, 10)
  out <- tibble(Metric=metName, pvalue=pval)
  return(out)
}

metNames <- c('Seat Belt - Rear','Seat Belt - Front','Seat Belt - Drive',
              'Interventions','Dangers','Distractions')
ttests <- tibble()
for (i in 1:length(outcomes)) {
  temp <- getPval(dat,outcomes[i],metNames[i])
  ttests <- bind_rows(temp, ttests)
}
kable(ttests)
```

* Important to note that the values below are **not** percentages. They are the mean values 
of the metrics described above. 
* We can see the campaign lead to significant progress in all of the metrics 
considered. Some of the effect sizes were likely capped because of where they began, 
for example, most people already always wear seat belts in the front seat, hence
we could only move the needle so much. 
```{r echo=FALSE}
pivotBars <- function(expid='group', pivot=NULL, title=NULL) {
  if (is.null(pivot)) {
    dat %>% 
      group_by_(expid) %>% 
      summarise(
        Distractions = mean(distraction_prone),
        Dangers = mean(considers_dangers),
        Interventions = mean(willing_intervene),
        `Seat Belt Drive` = mean(seatbelt_driver, na.rm=T),
        `Seat Belt Front` = mean(seatbelt_front, na.rm=T),
        `Seat Belt Rear` = mean(seatbelt_back, na.rm=T)
      ) %>%
      melt(id.var=c(expid)) %>%
      ggplot(.,aes(x=variable, y=value, fill=get(expid))) +
      geom_bar(stat='identity', position='dodge') +
      geom_text(aes(label=round(value, 3)), position = position_dodge(width = 1), size=4, hjust=0) +
      coord_flip() + ggtitle('Control vs. Experiment') +
      theme(legend.position='bottom', 
            legend.title=element_blank(), 
            axis.title.x=element_blank(),
            axis.title.y=element_blank(),
            plot.title = element_text(hjust = 0.5),
            axis.text.y = element_text(face="bold", size=16)) +
       scale_fill_manual(values=c('#000000',"#23b7fbff"))
  } else {
    dat %>% 
      group_by_(expid, pivot) %>% 
      summarise(
        Distractions = mean(distraction_prone),
        Dangers = mean(considers_dangers),
        Interventions = mean(willing_intervene),
        `Seat Belt Drive` = mean(seatbelt_driver, na.rm=T),
        `Seat Belt Front` = mean(seatbelt_front, na.rm=T),
        `Seat Belt Rear` = mean(seatbelt_back, na.rm=T)
      ) %>%
      melt(id.var=c(expid,pivot)) %>%
      ggplot(.,aes(x=get(pivot), y=value, fill=get(expid))) +
      geom_bar(stat='identity', position='dodge') +
      geom_text(aes(label=round(value, 3)), vjust=-0.25, position = position_dodge(width = 1), size=4) +
      ggtitle(paste0('Pivoted by ',title)) +
      facet_wrap(~variable) + 
      theme(legend.position='none',
            axis.title.x=element_blank(), 
            axis.title.y=element_blank(),
            plot.title = element_text(hjust = 0.5),
            axis.text.x = element_text(face="bold", size=13),
            axis.text.y = element_text(face="bold", size=16),
            strip.text.x = element_text(size = 18)) +
       scale_fill_manual(values=c('#000000',"#23b7fbff"))
  }
}

pivotBars(expid='group') %>% print()
```



###Digging deeper
#####Distribution shifts in outcomes
**Seatbelt:** Across the board we see a higher percentage of individuals always wearing 
seat belts, regardless of where they are seated.

**Dangers:** We see about 55% of respondents in the control group saw all three
(driving in front or back and engaging in distracted behaviors) as being very 
dangerous vs 75% of repsondents in the experiment group.

**Interventions:** We see that 20% of respondents in the experiment group were 
willing to take the strongest intervention in both situations, vs. 10% of respondents 
in the control group.

**Distractions:** We see that 17.5% of respondents in the control group acknowledged
all the items that could be considered a distraction, vs. 26% of those in the experiment
group. Top distractions both groups are using your mobile device and personal grooming.
The fact that the top are same for both groups suggests the effect was distributed across
distraction types.

**Across all key metrics, participants are consistently nudged from lower levels to higher levels.**   
```{r echo=FALSE, warning=FALSE}
getProportions <- function(dat, outcome, expid=NULL) {
  
  split <- strsplit(outcome, '_')[[1]]
  proportions <-
    dat %>% 
    group_by_(expid, outcome) %>% 
    summarise(count = n()) %>% 
    filter(!is.na(get(outcome))) %>% 
    mutate(Proportion = round(count/sum(count), 3),
           outcome = as.factor(round(get(outcome), 3)))
  if (grepl('distract', outcome)) {
    proportions$outcome <- factor(proportions$outcome, levels=c(as.character(seq(1,12,1))))
  }
  labels = c('Never/Almost Never', 'Less than Half', 'Most Times', 'Always')
  if (grepl('seatbelt',outcome)) {
    ggplot(proportions, aes(x=outcome, y=Proportion, fill=get(expid))) + 
      geom_bar(stat='identity', position='dodge', width=1.1) +
      labs(x='', y='',
           title = 
             paste0('Wear ', 
                    firstLetterUpper(split[1]), ' - ', 
                    firstLetterUpper(split[2])
             )
      ) +
      scale_x_discrete(labels=c(labels)) + 
      theme(legend.position="none", 
            plot.title = element_text(hjust = 0.5))
  } else {
    p <- 
      ggplot(proportions, aes(x=outcome, y=Proportion, fill=get(expid))) +
      geom_bar(stat='identity', position='dodge', width=1) +
      labs(x='', y='') + 
      theme(legend.position="none", 
            plot.title = element_text(hjust = 0.5)) + 
      scale_y_continuous(breaks=pretty_breaks(8))
    if (grepl('inter', outcome)) {
      p <- p + ggtitle('Strength of Intervention')
    } else if (grepl('danger',outcome)) {
      p <- p + ggtitle('Acknowledgement of Dangers')
    } else {
      proportions %<>% 
        filter(outcome != '12')
      p <- 
        ggplot(proportions, aes(x=outcome, y=Proportion, fill=get(expid))) +
        geom_bar(stat='identity', position='dodge', width=1) +
        labs(x='', y='') + 
        theme(legend.position="none", 
              plot.title = element_text(hjust = 0.5)) + 
        scale_y_continuous(breaks=pretty_breaks(8))
      p <- p + ggtitle('Distractions Acknowledged')
    }
  }
}

histOutcomes <- c('seatbelt_driver','seatbelt_front',
                  'seatbelt_back','willing_intervene',
                  'considers_dangers','distraction_sums')
for (i in 1:length(histOutcomes)) {
  getProportions(dat, histOutcomes[i], expid='group') %>% 
    print()
}
```



###Comparison across key pivots

####Estimated campaign impact on key sub-populations
* Identified most important pivots as being 
    + **For number of items considered distractions:** Not having license(-) and identifying as male(-).
    + **For how dangerous it is to not wear seat belt or drive while distracted:** Identifying as male(-).
    + **For intervention severity:** Identifying as male(-), having a limited or no license(+), 
    driving every day(+)
    + **For wearing a seat belt while driving:** Age(-), not driving(-), driving infrequently(+)
    + **For wearing a seat belt in the passenger seat:** Age(-), living in a suburban region(+), 
    driving a truck(-), driving daily(-)
    + **For wearing a seat belt in back seats:** Age(-)
* Overall, men are less responsive to the campaign across all metrics.
Age also appears to be a driver of seatbelt usage, showing an inverse relationship. 
The only other consistent driver appears to driving infrequently and/or not having
a license. 
```{r echo=FALSE}
for (i in 1:length(controls)) {
  pivotBars(controls[i], titles[i],expid = 'group') %>% 
    print()
}
```

```{r echo=FALSE}
dat %>% 
  group_by(group, age) %>% 
  summarise(
    considerDistraction = mean(distraction_prone),
    considerDangers = mean(considers_dangers),
    willingIntervene = mean(willing_intervene),
    wearSeatbelt.Drive = mean(seatbelt_driver, na.rm=T),
    wearSeatbelt.Front = mean(seatbelt_front, na.rm=T),
    wearSeatbelt.Back = mean(seatbelt_back, na.rm=T)
  ) %>%
  melt(id.var=c('group','age')) %>%
  ggplot(.,aes(x=age, y=value, colour=group)) +
  geom_point() + 
  geom_smooth(method='lm', linetype='dotted', size=.8, se=F) +
  geom_line() +
  scale_x_continuous(breaks=pretty_breaks(8)) +
  facet_wrap(~variable) + 
  ggtitle('Age') + 
  theme(plot.title = element_text(hjust = 0.5),
        legend.title=element_blank()) + 
  scale_color_manual(values=c('#000000',"#23b7fbff"))
```


```{r echo=FALSE}
regcontrols <- c('age','gender','region','license','vehicle','driving_freq','group')
outcomes <- c('distraction_prone','considers_dangers','willing_intervene',
              'seatbelt_driver','seatbelt_front','seatbelt_back')

f <- as.formula(paste0(outcomes[1], '~', paste(regcontrols, collapse="+")))
modDistract <- lm(f, dat)
out <- list()
for (i in 1:length(outcomes)) {
  f <- as.formula(paste0(outcomes[i], '~', paste(regcontrols, collapse="+")))
  mod <- lm(f, dat)
  d <- tidy(mod)
  d$p.value <- round(d$p.value, 4)
  d$significance <- ifelse(d$p.value <= 0.01, '**', 
                           ifelse(d$p.value <= 0.05, '*', ''))
  temp <- list(d)
  out[outcomes[i]] <- temp
}

```



###Estimated aggregate campaign impact

We compute the aggregate campaign impact by first capturing the mean value across
key metrics in the control group. We then build a model to predict the outcome
controlling for the all the pivots identified above. The coefficient for being 
in the experiment group can then be considered the expect change in behavior
for the metric in question, after applying control. We add this number to the 
average, which gives us a sense of how each behavior would shift, in aggregate,
if the general population was pushed through the campaign.
```{r  warning=FALSE, message=FALSE, echo=FALSE}
effects <- tibble()
for (i in 1:length(out)) {
  temp <- 
    out[[i]] %>% 
    filter(term=='groupexperiment') %>% 
    select(estimate) %>% 
    bind_cols(tibble(metric = names(out[i])))
  effects <- effects %>% bind_rows(temp)
}
varnames <- c('Distractions','Dangers','Interventions', 
              'Seatbelt.Drive','Seatbelt.Front','Seatbelt.Back')
impacts <- 
  dat %>% 
  filter(Group=='Control') %>% 
  summarise(
    distraction_prone = mean(distraction_prone),
    considers_dangers = mean(considers_dangers),
    willing_intervene = mean(willing_intervene),
    seatbelt_driver = mean(seatbelt_driver, na.rm=T),
    seatbelt_front = mean(seatbelt_front, na.rm=T),
    seatbelt_back = mean(seatbelt_back, na.rm=T)
  ) %>% 
  melt(value.name = 'Average') %>% 
  rename('metric' = 'variable') %>% 
  left_join(effects) %>% 
  mutate(
    Campaign = Average+estimate,
    Metric = varnames
    ) %>% 
  melt(id.vars='Metric', measure.vars=c('Average','Campaign'))

ggplot(impacts, aes(x=Metric, y=value, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +
  geom_text(aes(label=round(value,3)), vjust = -0.5, position = position_dodge(width = 1), size=2) +
  theme(legend.title=element_blank())
```


###Outstanding analyses
* How do campaign effects diminish over time, if at all?
* Is there a difference in behavior among regular signups and folks who signed
up after seeing a poster?
* Look at responses in the flow, are choices different as you go through the various flows
    + How do responses vary by terminal node in decision tree
* Can we understand **why** it is so effective for a given sub-population
* How many people **will not die**
* What do we do with this information with respect to campaigns going forward
    + Should we start by educating on the dangers of these activities
* Looping in CTD findings. What is the overall narrative?
    + Would help with the why
    + Could we have asked more interesting questions around speeding?
* What about external distractions?

###Next Steps
* What do we wish we had so we could dig even deeper?
* Forgetting GM, how does this info help DS campaigns?
* Bring this up at mgmt meeting